---
title: "Data Wrangling"
author: "Brandi Pessman"
date: "2024-10-15"
output: html_document
---

# Load Libraries

```{r libraries}
library(tidyverse) # for wrangling data
```

# Spider's Responses to Pure Tone Frequencies

```{r import freq response}
freq_response_attack <- read.csv("data/frequency_response_attack.csv") %>% 
  dplyr::select(SpiderID:hz1000) %>% 
  pivot_longer(cols = c(hz100:hz1000), values_to = "react", names_to = "frequency") %>% 
  mutate(frequency = fct_recode(frequency, "100" = "hz100",
                                "200" = "hz200",
                                "300" = "hz300",
                                "400" = "hz400",
                                "500" = "hz500",
                                "600" = "hz600",
                                "700" = "hz700",
                                "800" = "hz800",
                                "900" = "hz900",
                                "1000" = "hz1000")) %>% 
    #filter(Rest_Days > 7) %>% 
  mutate(treatment = ifelse(treatment == "", Experiment, treatment),
         frequency = as.character(frequency),
         frequency = as.numeric(frequency),
         Site = factor(Site),
         Year = factor(Year),
         Location = factor(Location),
         treatment = factor(treatment),
         SpiderID = factor(SpiderID),
         Site = fct_relevel(Site, "Rural", "Urban"))
```

```{r import freq response order}
freq_response_order <- read.csv("data/frequency_response_attack.csv") %>% 
  dplyr::select(SpiderID:Playback, order1:order10) %>% 
  mutate(frequency1 = ifelse(Playback == 1, 900,
                     ifelse(Playback == 2, 800,
                     ifelse(Playback == 3, 200,
                     ifelse(Playback == 4, 1000,
                     ifelse(Playback == 5, 700,
                     ifelse(Playback == 6, 500, 
                     ifelse(Playback == 7, 100,
                     ifelse(Playback == 8, 300, 
                     ifelse(Playback == 9, 600, 
                     ifelse(Playback == 10, 400, NA))))))))))) %>% 
  mutate(treatment = ifelse(treatment == "", Experiment, treatment),
         Site = factor(Site),
         Year = factor(Year),
         Location = factor(Location),
         treatment = factor(treatment),
         SpiderID = factor(SpiderID),
         Site = fct_relevel(Site, "Rural", "Urban"))
```


# Playback Conditions During Web Construction

```{r playback}
datapath = "/Users/bjpessman/Documents/phd_research_code/Vibration_Transmission/playback"
setwd(datapath)
txt_files_ls = list.files(path = datapath, pattern = "*.txt")
txt_files_df <- lapply(txt_files_ls,
                       function(x){
                         read.table(file = x, header = TRUE, sep ="\t")
                         })
for (i in 1:length(txt_files_df)){
  txt_files_df[[i]] <- cbind(txt_files_df[[i]],txt_files_ls[i])
  }
playback <- do.call("rbind", lapply(txt_files_df, as.data.frame))
playback <- playback %>%
  dplyr::select(Low.Freq..Hz., Inband.Power..dB.FS., `txt_files_ls[i]`)
colnames(playback) <- c("Low_Freq", "Power", "File")
playback <- playback %>%
  separate_wider_delim(cols = File, names = c("Name", "Ext"), ".") %>%
  separate_wider_delim(cols = Name, names = c("Rec", "Treatment"), "_") %>%
  dplyr::select(Rec, Treatment, Low_Freq, Power)

quiet <- playback %>%
  filter(Treatment == "ambient" | Treatment == "quiet") %>%
  pivot_wider(names_from = "Treatment", values_from = "Power") %>%
  mutate(ambient_u = 10^(ambient/10),
         quiet_u = 10^(quiet/10),
         snr_u = (quiet_u - ambient_u)/ambient_u,
         snr_db = 10 * log10(snr_u),
         Treatment = "Quiet") %>%
  dplyr::select(Rec, Low_Freq, Treatment, snr_db)

loud <- playback %>%
  filter(Treatment == "ambient" | Treatment == "loud") %>%
  pivot_wider(names_from = "Treatment", values_from = "Power") %>%
  mutate(ambient_u = 10^(ambient/10),
         loud_u = 10^(loud/10),
         snr_u = (loud_u - ambient_u)/ambient_u,
         snr_db = 10 * log10(snr_u),
         Treatment = "Loud") %>%
  dplyr::select(Rec, Low_Freq, Treatment, snr_db)

playback <- rbind(quiet, loud) %>%
  mutate(Treatment = fct_relevel(Treatment, "Quiet", "Loud"))
```

```{r playback removed}
playback_removed1 <- playback %>%
  group_by(Rec, Treatment) %>%
  summarize(sum_na = sum(is.na(snr_db))) # dropped 901 rows from 12 trials (mostly from quiet because the quiet treatment could be louder than ambient at times)
playback_removed2 <- playback %>%
  filter(snr_db < 0) %>%
  drop_na() %>%
  group_by(Rec, Treatment) %>%
  count() # dropped 734 rows from 11 trials (mostly from quiet)
playback_removed <- full_join(playback_removed1, playback_removed2) %>%
  mutate(sum_zero = n) %>%
  dplyr::select(-n)
playback_removed[is.na(playback_removed)] <- 0
playback_removed <- playback_removed %>%
  mutate(sum = sum_na + sum_zero)

playback <- playback %>%
  drop_na() %>%
  filter(! snr_db < 0) %>%
  mutate(Treatment = fct_relevel(Treatment, "Quiet", "Loud"))
```

# Measuring Web Vibration Transmission

## 1. Calculate the signal-to-noise ratio applied by the stimulus at point of contact with the web.

We used the laser vibrometer to record from the surface of the stimulus as it produced vibrations. We subtracted the power recorded during silent conditions to remove background noise.

```{r stimulus}
stimulus <- read.csv("data/stimulus.csv") %>% 
  mutate(
         # convert ambient and test to linear units
         Power_ambient_u = 10^(Power_ambient/10),
         Power_test_u = 10^(Power_test/10),
         # calculate linear snr
         snr_u_stim = (Power_test_u - Power_ambient_u)/Power_ambient_u,
         # convert to logarithmic snr
         snr_db_stim = 10 * log10(snr_u_stim),
         # rename some columns to clean up later code
         Power_ambient_stim = Power_ambient,
         Power_test_stim = Power_test) %>% 
  dplyr::select(Low_Freq, Power_ambient_stim, Power_test_stim, snr_u_stim, snr_db_stim)
```

```{r dropped stimulus values}
stimulus %>% # one dropped Low_Freq = 91.5
  filter(is.na(snr_db_stim)) 
stimulus %>% # one dropped Low_Freq = 86.1
  filter(snr_db_stim < 0)

stimulus <- stimulus %>% 
  filter(! snr_db_stim < 0) %>% 
  drop_na()
```

## 2. Import test and ambient data from the trials.

### Import Test Data 

Test = recording *during* the playback signal.

```{r test data}
datapath = "/Users/bjpessman/Documents/phd_research_code/Vibration_Transmission/text_files_5_38hz"
setwd(datapath)
getwd()
txt_files_ls = list.files(path = datapath, pattern = "*.txt")
txt_files_df <- lapply(txt_files_ls,
                       function(x){
                         read.table(file = x, header = TRUE, sep ="\t")
                         })
for (i in 1:length(txt_files_df)){
  txt_files_df[[i]] <- cbind(txt_files_df[[i]],txt_files_ls[i])
  }
main <- do.call("rbind", lapply(txt_files_df, as.data.frame))
main <- main %>%
  dplyr::select(Low.Freq..Hz., Inband.Power..dB.FS., `txt_files_ls[i]`)
colnames(main) <- c("Low_Freq", "Power", "File")
main <- main %>%
  separate_wider_delim(cols = File, names = c("Name", "Ext"), ".") %>%
  separate_wider_delim(cols = Name, names = c("SpiderID", "Location"), "_") %>%
  separate(col = Location, into = c("Position", "Trial"), sep = -1) %>%
  separate(col = Position, into = c("Distance", "Position"), sep = -1) %>%
  dplyr::select(SpiderID, Distance, Position, Trial, Low_Freq, Power)

test_Power <- main %>%
  drop_na() %>%
  mutate(Power_test_trial = Power) %>%
  dplyr::select(-Power)
```

### Import Ambient Data

Ambient = silence *before* the playback signal. 

```{r ambient data}
datapath = "/Users/bjpessman/Documents/phd_research_code/Vibration_Transmission/text_files_5_38hz_ambient"
setwd(datapath)
txt_files_ls = list.files(path = datapath, pattern = "*.txt")
txt_files_df <- lapply(txt_files_ls,
                       function(x){
                         read.table(file = x, header = TRUE, sep ="\t")
                         })
for (i in 1:length(txt_files_df)){
  txt_files_df[[i]] <- cbind(txt_files_df[[i]],txt_files_ls[i])
  }
main <- do.call("rbind", lapply(txt_files_df, as.data.frame))
main <- main %>%
  dplyr::select(Low.Freq..Hz., Inband.Power..dB.FS., `txt_files_ls[i]`)
colnames(main) <- c("Low_Freq", "Power", "File")
main <- main %>%
  separate_wider_delim(cols = File, names = c("Name", "Ext"), ".") %>%
  separate_wider_delim(cols = Name, names = c("SpiderID", "Location"), "_") %>%
  separate(col = Location, into = c("Position", "Trial"), sep = -1) %>%
  separate(col = Position, into = c("Distance", "Position"), sep = -1) %>%
  dplyr::select(SpiderID, Distance, Position, Trial, Low_Freq, Power)

ambient_Power <- main %>%
  drop_na() %>%
  mutate(Power_ambient_trial = Power) %>%
  dplyr::select(-Power)
```

## 3. Calculate the signal-to-noise ratio of the recorded signal at different areas on the web

We used a laser vibrometer to record vibrations from the surface of the web while the stimulus played vibrations on the web.

```{r correct}
# subtract ambient from test measures
main <- full_join(test_Power, ambient_Power, by = c("SpiderID", "Distance", "Position", "Trial", "Low_Freq")) %>%
  mutate(
         # convert ambient and test to linear units
         Power_ambient_u = 10^(Power_ambient_trial/10),
         Power_test_u = 10^(Power_test_trial/10),
         # calculate linear snr
         snr_u_trial = (Power_test_u - Power_ambient_u)/Power_ambient_u,
         # convert to logarithmic snr
         snr_db_trial = 10 * log10(snr_u_trial)) %>%
  #filter(! Low_Freq < 20) %>% # drops 4320 rows (4 Low_Freq x 60 Spiders * 18 trials)
  dplyr::select(SpiderID, Distance, Position, Trial, Low_Freq, Power_ambient_trial, Power_test_trial, snr_u_trial, snr_db_trial) 
```

```{r removed}
main_removed1 <- main %>%
  group_by(SpiderID, Distance, Position, Trial) %>%
  summarize(sum_na = sum(is.na(snr_db_trial))) 
sum(main_removed1$sum_na)
mean(main_removed1$sum_na) # 19231 dropped across 1080 trials (avg 17.8 per trial); these are instances where the background noise was greater than the recording (log10 of <= 0)
main_removed2 <- main %>%
  drop_na() %>%
  filter(snr_db_trial < 0) %>%
  group_by(SpiderID, Distance, Position, Trial) %>%
  count()
sum(main_removed2$n)
mean(main_removed2$n)# 33560 dropped across 1065 trials (avg 31.5 per trial); these are instances where the background noise nearly equalled the recording (log10 of 0.001-0.999)
main_removed <- full_join(main_removed1, main_removed2) %>%
  mutate(sum_zero = n) %>%
  dplyr::select(-n)
main_removed[is.na(main_removed)] <- 0
main_removed <- main_removed %>%
  mutate(sum = sum_na + sum_zero)

main <- main %>%
  drop_na() %>%
  filter(! snr_db_trial < 0)

example <- main %>% 
  filter(SpiderID == "ap109", 
         Distance == "close",
         Position == "a",
         Trial == "1")
```

## 4. Add information about the silk

```{r silk}
spiders <- read.csv("/Users/bjpessman/Documents/phd_research_code/Vibration_Transmission/data/treatments_assigned_20230905.csv", header = TRUE) %>% 
  filter(!Site == "Isolated")

# calculate condition
rownames(spiders) <- c(spiders$SpiderID)
cond <- data.frame(cbind(condition = residuals(lm(log(mass_mg) ~ log(ceph_width_mm), data = spiders)),
                         SpiderID = names(residuals(lm(log(mass_mg) ~ log(ceph_width_mm), data = spiders)))))
# add condition to the dataset
spiders <- full_join(spiders, cond, by = "SpiderID") %>% 
  mutate(condition = as.numeric(condition)) %>% 
  unite("Site_Treatment", c(Site, treatment), sep = "_", remove = FALSE)

main <- left_join(main, spiders, by = "SpiderID")

main <- unite(data = main, col = "unique", SpiderID:Trial, remove = FALSE)
```

## 5. Combine stimulus and trial datasets

```{r combine}
main <- left_join(main, stimulus, by = "Low_Freq") %>% 
  mutate(Site = factor(Site),
         treatment = factor(treatment)) %>% 
  unite("Dist_Pos", Distance:Position, sep = "_", remove = FALSE)
```

## 6 (Method 1) Calculate the energy loss and  average across spiders using logarithmic units

```{r energy loss 1}
vibration_transmission <- main %>% 
  mutate(snr_db = 10 * log10(snr_u_trial/snr_u_stim))
```

```{r removed 1}
vibration_transmission_removed <- vibration_transmission %>%
  group_by(SpiderID, Distance, Position, Trial) %>%
  summarize(sum_na = sum(is.na(snr_db)))
sum(vibration_transmission_removed$sum_na)
 # dropped 1817 because stimulus had been dropped at that Low_Freq (86.1 or 91.5)

vibration_transmission <- vibration_transmission %>% 
  drop_na(snr_db)
```

```{r check position 1}
#positions - overall
distances <- vibration_transmission %>% 
  group_by(Low_Freq, Site, treatment, Dist_Pos) %>% 
  summarize(mean_snr = mean(snr_db),
            se_snr = plotrix::std.error(snr_db)) %>% 
  mutate(treatment = factor(treatment),
         treatment= fct_relevel(treatment, "Quiet", "Loud"),
         Dist_Pos = fct_recode(Dist_Pos, "Short A" = "close_a", "Short B" = "close_b", "Short C" = "close_c", "Longer A" = "far_a", "Longer B" = "far_b", "Longer C" = "far_c"),
         Dist_Pos = fct_relevel(Dist_Pos, "Short A", "Longer A", "Short B", "Longer B", "Short C", "Longer C")) 

size = 16
treatment.labs <- c("Quiet (4 Days)", "Loud (4 Days)")
names(treatment.labs) <- c("Quiet", "Loud")
ggplot() +
  geom_line(aes(x = Low_Freq, y = mean_snr, group = Dist_Pos, color = Dist_Pos), alpha = 0.2, data = distances, linewidth = 0.25) +
  geom_smooth(aes(x = Low_Freq, y = mean_snr, group = Dist_Pos, color = Dist_Pos, fill = Dist_Pos), data = distances, method = "loess", linewidth = 0.5) +
  xlab("Frequency (Hz)") +
  ylab("Energy Loss through Web Transmission (∆ dB)") +
  labs(fill = "", color = "") +
  scale_color_manual("", values = c("darkred", "blue", "darkorange", "darkgreen", "gold3", "purple")) +
  scale_fill_manual("", values = c("darkred", "blue", "darkorange", "darkgreen", "gold3", "purple")) +
  scale_x_continuous(limits = c(20, 2250), breaks = c(20, 500, 1000, 1500, 2000), expand = c(0,0)) +
  scale_y_continuous(limits = c(-75, 20), breaks = c(seq(-60, 20, 20)), expand = c(0,0)) +
  #scale_x_continuous(limits = c(20, 1000), breaks = c(20, 250, 500, 750, 1000), expand = c(0,0)) +
  #scale_y_continuous(limits = c(-60, 20), breaks = c(seq(-50, 20, 10)), expand = c(0,0)) +
  theme_classic() +
  theme(axis.text = element_text(size = size, color = "black", family = "sans"),
        axis.title = element_text(size = size, color = "black", family = "sans"),
        legend.text = element_text(size = size, color = "black", family = "sans"),
        legend.title = element_text(size = size, color = "black", family = "sans"),
        strip.text = element_text(size = size, color = "black", family="sans"),
        legend.position = "top") +
  facet_grid(Site ~ treatment, labeller = labeller(treatment = treatment.labs))

```

```{r average 1}
vibration_transmission <- vibration_transmission %>% 
  group_by(SpiderID, Low_Freq, Distance, Site, treatment, Site_Treatment, trial_age, mass_mg, condition, wet_mg, dry_mg, moisture_per) %>% 
  # average across spider using linear units since positions did not differ (step 6, method 2)
  summarise(spider_snr_db = mean(snr_db)) %>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"),
         Site = factor(Site), 
         Site = fct_relevel(Site, "Rural", "Urban"),
         SpiderID = factor(SpiderID),
         Low_Freq = as.numeric(Low_Freq),
         Site_Treatment = factor(Site_Treatment),
         Site_Treatment = fct_relevel(Site_Treatment, "Rural_Quiet", "Rural_Loud", "Urban_Quiet", "Urban_Loud")) %>% 
  ungroup()
```

## 6 (Method 2) Average across positions and spiders using linear units and calculate energy loss 

```{r average and energy loss 2}
vibration_transmission_position2 <- main %>% 
  group_by(SpiderID, Low_Freq, Distance, Position, Dist_Pos, Site, treatment, Site_Treatment, trial_age, mass_mg, condition, wet_mg, dry_mg, moisture_per, snr_u_stim) %>% 
  # average across spider and position using linear units
  summarise(position_snr_u = mean(snr_u_trial)) %>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"),
         Site = factor(Site), 
         Site = fct_relevel(Site, "Rural", "Urban"),
         SpiderID = factor(SpiderID),
         Low_Freq = as.numeric(Low_Freq),
         Site_Treatment = factor(Site_Treatment),
         Site_Treatment = fct_relevel(Site_Treatment, "Rural_Quiet", "Rural_Loud", "Urban_Quiet", "Urban_Loud")) %>% 
  ungroup() %>% 
  # convert to logarithmic snr
  mutate(position_snr_db = 10 * log10(position_snr_u/snr_u_stim))
```

```{r check position 2}
#positions - overall
distances2 <- vibration_transmission_position2 %>% 
  group_by(Low_Freq, Site, treatment, Dist_Pos) %>% 
  summarize(mean_snr = mean(position_snr_db),
            se_snr = plotrix::std.error(position_snr_db)) %>% 
  mutate(treatment = factor(treatment),
         treatment= fct_relevel(treatment, "Quiet", "Loud"),
         Dist_Pos = fct_recode(Dist_Pos, "Short A" = "close_a", "Short B" = "close_b", "Short C" = "close_c", "Longer A" = "far_a", "Longer B" = "far_b", "Longer C" = "far_c"),
         Dist_Pos = fct_relevel(Dist_Pos, "Short A", "Longer A", "Short B", "Longer B", "Short C", "Longer C")) 

size = 16
treatment.labs <- c("Quiet (4 Days)", "Loud (4 Days)")
names(treatment.labs) <- c("Quiet", "Loud")
ggplot() +
  geom_line(aes(x = Low_Freq, y = mean_snr, group = Dist_Pos, color = Dist_Pos), alpha = 0.2, data = distances2, linewidth = 0.25) +
  geom_smooth(aes(x = Low_Freq, y = mean_snr, group = Dist_Pos, color = Dist_Pos, fill = Dist_Pos), data = distances2, method = "loess", linewidth = 0.5) +
  xlab("Frequency (Hz)") +
  ylab("Energy Loss through Web Transmission (∆ dB)") +
  labs(fill = "", color = "") +
  scale_color_manual("", values = c("darkred", "blue", "darkorange", "darkgreen", "gold3", "purple")) +
  scale_fill_manual("", values = c("darkred", "blue", "darkorange", "darkgreen", "gold3", "purple")) +
  scale_x_continuous(limits = c(20, 2250), breaks = c(20, 500, 1000, 1500, 2000), expand = c(0,0)) +
  scale_y_continuous(limits = c(-75, 20), breaks = c(seq(-60, 20, 20)), expand = c(0,0)) +
  #scale_x_continuous(limits = c(20, 1000), breaks = c(20, 250, 500, 750, 1000), expand = c(0,0)) +
  #scale_y_continuous(limits = c(-60, 20), breaks = c(seq(-50, 20, 10)), expand = c(0,0)) +
  theme_classic() +
  theme(axis.text = element_text(size = size, color = "black", family = "sans"),
        axis.title = element_text(size = size, color = "black", family = "sans"),
        legend.text = element_text(size = size, color = "black", family = "sans"),
        legend.title = element_text(size = size, color = "black", family = "sans"),
        strip.text = element_text(size = size, color = "black", family="sans"),
        legend.position = "top") +
  facet_grid(Site ~ treatment, labeller = labeller(treatment = treatment.labs))
#700 x 600
```

```{r average 2}
vibration_transmission2 <- main %>% 
  group_by(SpiderID, Low_Freq, Distance, Site, treatment, Site_Treatment, trial_age, mass_mg, condition, wet_mg, dry_mg, moisture_per, snr_u_stim) %>% 
  # average across spider using linear units since positions did not differ (step 6, method 2)
  summarise(spider_snr_u = mean(snr_u_trial)) %>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"),
         Site = factor(Site), 
         Site = fct_relevel(Site, "Rural", "Urban"),
         SpiderID = factor(SpiderID),
         Low_Freq = as.numeric(Low_Freq),
         Site_Treatment = factor(Site_Treatment),
         Site_Treatment = fct_relevel(Site_Treatment, "Rural_Quiet", "Rural_Loud", "Urban_Quiet", "Urban_Loud")) %>% 
  ungroup() %>% 
  # convert to logarithmic snr
  mutate(spider_snr_db = 10 * log10(spider_snr_u/snr_u_stim))
```

```{r removed 2}
vibration_transmission2_removed <- vibration_transmission2 %>%
  group_by(SpiderID, Distance) %>%
  summarize(sum_na = sum(is.na(spider_snr_db)))
sum(vibration_transmission2_removed$sum_na)
 # dropped 239 because stimulus had been dropped at that Low_Freq (86.1 or 91.5)

vibration_transmission2 <- vibration_transmission2 %>% 
  drop_na(spider_snr_db)
```

# Save

```{r save}
saveRDS(freq_response_attack, file = "wrangled_data/freq_response_attack.rds")
saveRDS(freq_response_order, file = "wrangled_data/freq_response_order.rds")
saveRDS(playback, file = "wrangled_data/playback.rds")
saveRDS(example, file = "wrangled_data/example.rds")
saveRDS(stimulus, file = "wrangled_data/stimulus.rds")
saveRDS(vibration_transmission, file = "wrangled_data/vibration_transmission.rds")
saveRDS(vibration_transmission2, file = "wrangled_data/vibration_transmission2.rds")
```