---
title: "transmission_analysis"
author: "Brandi Pessman"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, include = FALSE}
library(tidyverse)
library(lme4) #lmer
library(MASS) #glm.nb
library(broom.mixed) #augment
library(betareg)
library(ggpubr) #ggarrange
library(emmeans) # post hoc
library(effects)
library(lubridate)
library(flextable)
#library(rstatix)

scale_this <- function(x){
  (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE)
}

center_this <- function(x){
  (x - mean(x, na.rm=TRUE))
}

bootStrap <- function(mm) {
    predict(mm, newdata = nd, re.form = ~0, type = "response")
}

treatment.labs <- c("Quiet (4 Days)", "Loud (4 Days)")
names(treatment.labs) <- c("Quiet", "Loud")

group.labs <- c("2022", "2023 - Quiet", "2023 - Loud")
names(group.labs) <- c("2022", "2023_Quiet", "2023_Loud")

options(scipen = 999)

range_min = 460
range_max = 640
```

```{r import test data, include = FALSE}
datapath = "/Users/bjpessman/Library/CloudStorage/OneDrive-UniversityofNebraska-Lincoln/PhD Research/Summer 2023/vibration_transmission/text_files_10hz"
setwd(datapath)
txt_files_ls = list.files(path = datapath, pattern = "*.txt")
txt_files_df <- lapply(txt_files_ls, 
                       function(x){
                         read.table(file = x, header = TRUE, sep ="\t")
                         })
for (i in 1:length(txt_files_df)){
  txt_files_df[[i]] <- cbind(txt_files_df[[i]],txt_files_ls[i])
  }
main <- do.call("rbind", lapply(txt_files_df, as.data.frame))
main <- main %>% 
  dplyr::select(Low.Freq..Hz., Leq..dB.FS., Inband.Power..dB.FS., `txt_files_ls[i]`) 
colnames(main) <- c("Low_Freq", "Leq", "Power", "File")
main <- main %>% 
  separate_wider_delim(cols = File, names = c("Name", "Ext"), ".") %>% 
  separate_wider_delim(cols = Name, names = c("SpiderID", "Location"), "_") %>% 
  separate(col = Location, into = c("Position", "Trial"), sep = -1) %>% 
  separate(col = Position, into = c("Distance", "Position"), sep = -1) %>% 
  dplyr::select(SpiderID, Distance, Position, Trial, Low_Freq, Leq, Power)

test <- main %>% 
  dplyr::select(SpiderID, Distance, Position, Trial, Low_Freq, Leq) %>% 
  drop_na() %>% 
  mutate(Leq_test = Leq) %>% 
  dplyr::select(-Leq)

# save ambient before after in a new dataframe
ambient_raw <- test %>% 
  filter(Distance == "ambient") %>% 
  unite(col = "unique", SpiderID:Trial, remove = FALSE) %>% 
  group_by(SpiderID, Distance, Position, Trial) %>% 
  mutate(centered_leq_test = center_this(Leq_test))

ambient_ba <- ambient_raw %>% 
  group_by(Low_Freq, Position) %>% 
  summarize(mean_leq = mean(centered_leq_test),
            sd_leq = sd(centered_leq_test),
            se_leq = plotrix::std.error(centered_leq_test))

# remove ambient measures from test
test <- test %>% 
  filter(! Distance == "ambient") 
```

```{r import ambient data, include = FALSE}
datapath = "/Users/bjpessman/Library/CloudStorage/OneDrive-UniversityofNebraska-Lincoln/PhD Research/Summer 2023/vibration_transmission/text_files_10hz_ambient"
setwd(datapath)
txt_files_ls = list.files(path = datapath, pattern = "*.txt")
txt_files_df <- lapply(txt_files_ls, 
                       function(x){
                         read.table(file = x, header = TRUE, sep ="\t")
                         })
for (i in 1:length(txt_files_df)){
  txt_files_df[[i]] <- cbind(txt_files_df[[i]],txt_files_ls[i])
  }
main <- do.call("rbind", lapply(txt_files_df, as.data.frame))
main <- main %>% 
  dplyr::select(Low.Freq..Hz., Leq..dB.FS., Inband.Power..dB.FS., `txt_files_ls[i]`) 
colnames(main) <- c("Low_Freq", "Leq", "Power", "File")
main <- main %>% 
  separate_wider_delim(cols = File, names = c("Name", "Ext"), ".") %>% 
  separate_wider_delim(cols = Name, names = c("SpiderID", "Location"), "_") %>% 
  separate(col = Location, into = c("Position", "Trial"), sep = -1) %>% 
  separate(col = Position, into = c("Distance", "Position"), sep = -1) %>% 
  dplyr::select(SpiderID, Distance, Position, Trial, Low_Freq, Leq, Power)

ambient <- main %>% 
  dplyr::select(SpiderID, Distance, Position, Trial, Low_Freq, Leq) %>% 
  drop_na() %>% 
  mutate(Leq_ambient = Leq) %>% 
  dplyr::select(-Leq)
```

```{r corrected leq, include = FALSE}
# subtract ambient from test measures
main <- full_join(test, ambient, by = c("SpiderID", "Distance", "Position", "Trial", "Low_Freq")) %>% 
  mutate(Leq = Leq_test - Leq_ambient) %>% 
  group_by(SpiderID, Distance, Position, Trial) %>% 
  mutate(centered_leq = center_this(Leq))
  
# import spiders dataframe with info about silk
spiders <- read.csv("/Users/bjpessman/Documents/phd_research_code/vibration_transmission/assigning_treatments/treatments_assigned_20230905.csv", header = TRUE)

main <- left_join(main, spiders, by = "SpiderID")
  
main <- unite(data = main, col = "unique", SpiderID:Trial, remove = FALSE)
```

```{r import field noise, include = FALSE}
datapath = "/Users/bjpessman/Library/CloudStorage/OneDrive-UniversityofNebraska-Lincoln/PhD Research/Summer 2023/vibration_transmission/field_noise"
setwd(datapath)
txt_files_ls = list.files(path = datapath, pattern = "*.txt")
txt_files_df <- lapply(txt_files_ls, 
                       function(x){
                         read.table(file = x, header = TRUE, sep ="\t")
                         })
for (i in 1:length(txt_files_df)){
  txt_files_df[[i]] <- cbind(txt_files_df[[i]],txt_files_ls[i])
  }
noise <- do.call("rbind", lapply(txt_files_df, as.data.frame))
noise <- noise %>% 
  dplyr::select(Low.Freq..Hz., Leq..dB.FS., `txt_files_ls[i]`) 
colnames(noise) <- c("Low_Freq", "Leq", "File")
noise <- noise %>% 
  separate_wider_delim(cols = File, names = c("Name", "Ext"), ".") %>% 
  separate_wider_delim(cols = Name, names = c("Site", "Visit", "Recorder"), "_") %>% 
  dplyr::select(Site, Visit, Recorder, Low_Freq, Leq) %>% 
  drop_na() 
```

```{r import frequency response, include = FALSE}
freq_response_all <- read.csv("data/frequency_response.csv")  %>% 
  dplyr::select(SpiderID:hz1000) %>% 
  filter(!Experiment == "Web") %>% 
  pivot_longer(cols = c(hz100:hz1000), values_to = "react", names_to = "frequency") %>% 
  mutate(frequency = fct_recode(frequency, "100" = "hz100",
                                "200" = "hz200",
                                "300" = "hz300",
                                "400" = "hz400",
                                "500" = "hz500",
                                "600" = "hz600",
                                "700" = "hz700",
                                "800" = "hz800",
                                "900" = "hz900",
                                "1000" = "hz1000"))

freq_response_attack <- read.csv("data/frequency_response_attack.csv") %>% 
  dplyr::select(SpiderID:hz1000)%>% 
  filter(!Experiment == "Web") %>% 
  pivot_longer(cols = c(hz100:hz1000), values_to = "react", names_to = "frequency") %>% 
  mutate(frequency = fct_recode(frequency, "100" = "hz100",
                                "200" = "hz200",
                                "300" = "hz300",
                                "400" = "hz400",
                                "500" = "hz500",
                                "600" = "hz600",
                                "700" = "hz700",
                                "800" = "hz800",
                                "900" = "hz900",
                                "1000" = "hz1000"))

freq_response_attack %>% 
  filter(! is.na(Rest_Days)) %>% 
  group_by(Year) %>% 
  summarize(mean_rest = mean(Rest_Days),
            mean_age = mean(Freq_Age))

isolated_all <- read.csv("data/isolated_all_response.csv")  %>% 
  pivot_longer(cols = c(f_100:f_1000), values_to = "react", names_to = "frequency") %>% 
  mutate(frequency = fct_recode(frequency, "100" = "f_100",
                                "200" = "f_200",
                                "300" = "f_300",
                                "400" = "f_400",
                                "500" = "f_500",
                                "600" = "f_600",
                                "700" = "f_700",
                                "800" = "f_800",
                                "900" = "f_900",
                                "1000" = "f_1000"))

isolated_attack <- read.csv("data/isolated_attacks.csv")  %>% 
  pivot_longer(cols = c(f_100:f_1000), values_to = "react", names_to = "frequency") %>% 
  mutate(frequency = fct_recode(frequency, "100" = "f_100",
                                "200" = "f_200",
                                "300" = "f_300",
                                "400" = "f_400",
                                "500" = "f_500",
                                "600" = "f_600",
                                "700" = "f_700",
                                "800" = "f_800",
                                "900" = "f_900",
                                "1000" = "f_1000"))
```

## Descriptives

**Sample Size **
```{r sample_size, echo = FALSE, message = FALSE}
main %>% 
  group_by(Site, treatment) %>% 
  count() %>% 
  mutate(n = n/200/18)
```

**Age and Condition**
```{r age and condition, echo = FALSE, message = FALSE}
spiders2 <- spiders %>% 
  filter(!Site == "Isolated") 

rownames(spiders2) <- c(spiders2$SpiderID)
cond <- data.frame(cbind(condition = residuals(lm(log(mass_mg) ~ log(ceph_width_mm), data = spiders2)),
                         SpiderID = names(residuals(lm(log(mass_mg) ~ log(ceph_width_mm), data = spiders2)))))
# add condition to the choice dataset
spiders2 <- full_join(spiders2, cond, by = "SpiderID") %>% 
  mutate(condition = as.numeric(condition))

spiders2 %>% 
  group_by(Site, treatment) %>% 
  summarize(mean_age = mean(trial_age),
            se_age = plotrix::std.error(trial_age),
            mean_cond = mean(condition),
            se_cond = plotrix::std.error(condition)) %>% 
  ggplot() +
  geom_point(aes(x = Site, y = mean_age, color = treatment)) +
  geom_errorbar(aes(x = Site, ymax = mean_age + se_age, ymin = mean_age - se_age, color = treatment))

spiders2 %>% 
  group_by(Site, treatment) %>% 
  summarize(mean_age = mean(trial_age),
            se_age = plotrix::std.error(trial_age),
            mean_cond = mean(condition),
            se_cond = plotrix::std.error(condition)) %>% 
  ggplot() +
  geom_point(aes(x = Site, y = mean_cond, color = treatment)) +
  geom_errorbar(aes(x = Site, ymax = mean_cond + se_cond, ymin = mean_cond - se_cond, color = treatment))

shapiro.test(rank(spiders2$trial_age))
car::Anova(lm(log(trial_age) ~ Site * treatment, data = spiders2))
trial_age <- glm.nb(trial_age ~ Site * treatment, data = spiders2)
car::Anova(trial_age)

shapiro.test(spiders2$condition)
car::Anova(lm(condition ~ Site * treatment, data = spiders2))
```

**Ambient Before vs. After**
```{r ambient_before_after, echo = FALSE, message = FALSE}
ggplot() +
  geom_line(aes(x = Low_Freq, y = mean_leq, group = Position, color = Position), data = ambient_ba, linewidth = 1) +
  geom_ribbon(aes(x = Low_Freq, ymin = mean_leq - se_leq, ymax = mean_leq + se_leq, group = Position, fill = Position), alpha = 0.5, data = ambient_ba) +
  xlab("Frequency (10 Hz Bins)") +
  ylab("Relative Amplitude (Centered Leq, dB)") +
  scale_fill_manual(values = c("#7570b3", "#e6ab02"),
                     labels = c("Before", "After")) +
  scale_color_manual(values = c("#7570b3", "#e6ab02"),
                     labels = c("Before", "After")) +
  theme_classic() +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 12, color = "black"),
        legend.position = "top")
```

**Close vs Far Overall**
```{r close_far, echo = FALSE, message = FALSE}
# positions - site x treatment
distances <- main %>% 
  filter(! Site == "Isolated") %>% 
  unite(col = "Dist_Pos", Distance:Position, remove = FALSE) %>% 
  group_by(Low_Freq, Site, treatment, Dist_Pos) %>% 
  summarize(mean_leq = mean(centered_leq),
            sd_leq = sd(centered_leq),
            se_leq = plotrix::std.error(centered_leq)) %>% 
  mutate(treatment = factor(treatment),
         treatment= fct_relevel(treatment, "Quiet", "Loud"),
         Dist_Pos = fct_recode(Dist_Pos, "Close A" = "close_a", "Close B" = "close_b", "Close C" = "close_c", "Far A" = "far_a", "Far B" = "far_b", "Far C" = "far_c"),
         Dist_Pos = fct_relevel(Dist_Pos, "Close A", "Far A", "Close B", "Far B", "Close C", "Far C"))

ggplot() +
  geom_line(aes(x = Low_Freq, y = mean_leq, group = Dist_Pos, color = Dist_Pos), data = distances) +
  geom_ribbon(aes(x = Low_Freq, ymin = mean_leq - se_leq, ymax = mean_leq + se_leq, group = Dist_Pos, fill = Dist_Pos), alpha = 0.5, data = distances) +
  xlab("Frequency (10 Hz Bins)") +
  ylab("Relative Amplitude (Mean Centered Leq, dB)") +
  labs(fill = "Position", color = "Position") +
  scale_y_continuous(limits = c(-15, 25), breaks = c(-10, 0, 10, 20), expand = c(0,0)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black"),
        axis.title = element_text(size = 14, color = "black"),
        legend.text = element_text(size = 14, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        legend.position = "top",
        strip.text = element_text(size = 14, color = "black", family="sans")) +
  facet_grid(Site ~ treatment, labeller = labeller(treatment = treatment.labs))

#positions - overall
distances <- main %>% 
  filter(! Site == "Isolated") %>% 
  unite(col = "Dist_Pos", Distance:Position, remove = FALSE) %>% 
  group_by(Low_Freq, Dist_Pos) %>% 
  summarize(mean_leq = mean(centered_leq),
            sd_leq = sd(centered_leq),
            se_leq = plotrix::std.error(centered_leq))

ggplot() +
  geom_line(aes(x = Low_Freq, y = mean_leq, group = Dist_Pos, color = Dist_Pos), data = distances) +
  geom_ribbon(aes(x = Low_Freq, ymin = mean_leq - se_leq, ymax = mean_leq + se_leq, group = Dist_Pos, fill = Dist_Pos), alpha = 0.5, data = distances) +
  xlab("Frequency (10 Hz Bins)") +
  ylab("Relative Amplitude \n(Mean Centered Leq, dB)") +
  labs(fill = "Distance_Position", color = "Distance_Position") +
  scale_y_continuous(limits = c(-10, 20), breaks = c(-10, 0, 10, 20), expand = c(0,0)) +
  theme_classic() +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 12, color = "black"))

# close/far - site x treatment
distances <- main %>% 
  filter(! Site == "Isolated") %>% 
  unite(col = "Dist_Pos", Distance:Position, remove = FALSE) %>% 
  group_by(Low_Freq, Site, treatment, Distance) %>% 
  summarize(mean_leq = mean(Leq),
            sd_leq = sd(Leq),
            se_leq = plotrix::std.error(Leq)) %>% 
  mutate(treatment = factor(treatment),
         treatment= fct_relevel(treatment, "Quiet", "Loud"))

ggplot() +
  geom_line(aes(x = Low_Freq, y = mean_leq, group = Distance, color = Distance), data = distances) +
  geom_ribbon(aes(x = Low_Freq, ymin = mean_leq - se_leq, ymax = mean_leq + se_leq, group = Distance, fill = Distance), alpha = 0.5, data = distances) +
  xlab("Frequency (10 Hz Bins)") +
  # only test - ambient
  ylab("Corrected Amplitude (Leq, dB)") +
  scale_fill_manual(values = c("black", "grey60"),
                     labels = c("Close", "Far")) +
  scale_color_manual(values = c("black", "grey60"),
                     labels = c("Close", "Far")) +
  scale_y_continuous(limits = c(0, 30), breaks = c(0, 10, 20, 30), expand = c(0,0)) +
  theme_classic() +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 12, color = "black"),
        strip.text = element_text(size = 12, color = "black", family="sans")) +
  facet_grid(Site ~ treatment, labeller = labeller(treatment = treatment.labs))

#close/far - overall
distances <- main %>% 
  filter(! Site == "Isolated") %>% 
  unite(col = "Dist_Pos", Distance:Position, remove = FALSE) %>% 
  group_by(Low_Freq, Distance) %>% 
  summarize(mean_leq = mean(Leq),
            sd_leq = sd(Leq),
            se_leq = plotrix::std.error(Leq))

ggplot() +
  annotate(geom = "rect", ymin = 0, ymax = 30, xmin = range_min, xmax = range_max, fill = "grey90") +
  geom_vline(xintercept = range_min, linetype = "dashed", color = "#1b9e77") +
  geom_vline(xintercept = range_max, linetype = "dashed", color = "#d95f02") +
  geom_line(aes(x = Low_Freq, y = mean_leq, group = Distance, color = Distance), data = distances) +
  geom_ribbon(aes(x = Low_Freq, ymin = mean_leq - se_leq, ymax = mean_leq + se_leq, group = Distance, fill = Distance), alpha = 0.5, data = distances) +
  xlab("Frequency (10 Hz Bins)") +
  # only test - ambient
  ylab("Corrected Amplitude (Leq, dB)") +
  scale_fill_manual(values = c("black", "grey60"),
                     labels = c("Close", "Far")) +
  scale_color_manual(values = c("black", "grey60"),
                     labels = c("Close", "Far")) +
  scale_y_continuous(limits = c(0, 30), breaks = c(0, 10, 20, 30), expand = c(0,0)) + 
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black"),
        axis.title = element_text(size = 14, color = "black"),
        legend.text = element_text(size = 14, color = "black"),
        legend.title = element_text(size = 14, color = "black"))
```

**Field Noise and Playback**
```{r field_noise_playback, eco = FALSE, message = FALSE}
noise_sum <- noise  %>% 
  group_by(Site, Low_Freq) %>% 
  summarize(mean_leq = mean(Leq),
            se_leq = plotrix::std.error(Leq))  %>% 
  mutate(Site = factor(Site),
         Site = fct_recode(Site, "Urban" = "campus", "Rural" = "popes"),
         Site = fct_relevel(Site, "Rural", "Urban"))

noise_sum %>% 
  filter(! Low_Freq < 20) %>% 
  ggplot() +
    annotate(geom = "rect", ymin = -95, ymax = -13, xmin = range_min, xmax = range_max, fill = "grey90") +
  geom_vline(xintercept = range_max, linetype = "dashed", color = "#d95f02") +
  geom_vline(xintercept = range_min, linetype = "dashed", color = "#1b9e77") +
  geom_line(aes(x = Low_Freq, y = mean_leq, color = Site), size = 1) +
  geom_ribbon(aes(x = Low_Freq, ymin = mean_leq - se_leq, ymax = mean_leq + se_leq, fill = Site), alpha = 0.5) +
  xlab("Frequency (10 Hz Bins)") +
  ylab("Amplitude (Leq, dB)\nQuieter <------------> Louder") +
  scale_color_manual("Collection Site", values = c("#1b9e77", "#d95f02")) +
  scale_fill_manual("Collection Site", values = c("#1b9e77", "#d95f02")) +
  scale_y_continuous(limits = c(-95, -13), breaks = c(-90, -75, -60, -45, -30, -15), expand = c(0,0)) +
  #scale_x_continuous(expand = c(0,0)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family = "sans"),
        axis.title = element_text(size = 14, color = "black", family = "sans"),
        legend.text = element_text(size = 14, color = "black", family = "sans"),
        legend.title = element_text(size = 14, color = "black", family = "sans"),
        legend.position = "top")

noise_sum_urban <- noise_sum %>% 
  filter(Site == "Urban",
         ! Low_Freq < 20)
urban_dY <- diff(noise_sum_urban$mean_leq)/diff(noise_sum_urban$Low_Freq) 
urban_dX <- rowMeans(embed(noise_sum_urban$Low_Freq,2))
derivativeData_u <- data.frame(X = urban_dX, Y = urban_dY, type = "Derivative", Site = "Urban")

noise_sum_rural <- noise_sum %>% 
  filter(Site == "Rural",
         ! Low_Freq < 20)
rural_dY <- diff(noise_sum_rural$mean_leq)/diff(noise_sum_rural$Low_Freq) 
rural_dX <- rowMeans(embed(noise_sum_rural$Low_Freq,2))
derivativeData_r <- data.frame(X = rural_dX, Y = rural_dY, type = "Derivative", Site = "Rural")

derivativeData <- rbind(derivativeData_u, derivativeData_r) 

derivativeData2 <- derivativeData %>% 
  pivot_wider(names_from = "Site", values_from = "Y") %>% 
  mutate(diff = round(Urban-Rural, 2))

ggplot(derivativeData, aes(X,Y, color = Site)) + 
  geom_line(size = 1) +
  geom_hline(yintercept = -0.0116700000, linetype = "dashed") +
  geom_hline(yintercept = -0.0129166667, linetype = "dashed") +

  geom_vline(xintercept = range_min, linetype = "dashed", color = "#1b9e77") +
  geom_vline(xintercept = range_max, linetype = "dashed", color = "#d95f02") +
  xlab("Frequency (10 Hz Bins)") +
  ylab("First Derivative of Amplitude/Frequency") +
  scale_color_manual("Collection Site", values = c("#1b9e77", "#d95f02")) +
  scale_y_continuous(limits = c(-0.2, 0.2)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family = "sans"),
        axis.title = element_text(size = 14, color = "black", family = "sans"),
        legend.text = element_text(size = 14, color = "black", family = "sans"),
        legend.title = element_text(size = 14, color = "black", family = "sans"),
        legend.position = "top")


#rural_dY2 <- diff(derivativeData_r$Y)/diff(derivativeData_r$X) 
#rural_dX2 <- rowMeans(embed(derivativeData_r$X,2))
#derivativeData_r2 <- data.frame(X2 = rural_dX2, Y2 = rural_dY2, type = "Derivative2", Site = "Rural")

#urban_dY2 <- diff(derivativeData_u$Y)/diff(derivativeData_u$X) 
#urban_dX2 <- rowMeans(embed(derivativeData_u$X,2))
#derivativeData_u2 <- data.frame(X2 = urban_dX2, Y2 = urban_dY2, type = "Derivative2", Site = "Urban")

#derivativeData2 <- rbind(derivativeData_u2, derivativeData_r2) 

#ggplot(derivativeData2, aes(X2,Y2, color = Site)) + 
#  geom_line(size = 1) +
#  geom_hline(yintercept = 0.000095, linetype = "dashed") +
#  geom_hline(yintercept = 0, linetype = "dashed") +
#  geom_vline(xintercept = 380, linetype = "dashed", color = #"#1b9e77") +
#  geom_vline(xintercept = 740, linetype = "dashed", color = #"#d95f02") +
#  xlab("Frequency (10 Hz Bins)") +
#  ylab("Second Derivative of Amplitude/Frequency") +
#  scale_color_manual("Collection Site", values = c("#1b9e77", #"#d95f02")) +
#  theme_classic() +
#  scale_y_continuous(limits = c(-0.0010, 0.0010)) +
#  theme(axis.text = element_text(size = 14, color = "black", #family = "sans"),
#        axis.title = element_text(size = 14, color = "black", #family = "sans"),
#        legend.text = element_text(size = 14, color = #"black", family = "sans"),
#        legend.title = element_text(size = 14, color = #"black", family = "sans"),
#        legend.position = "top")


playback <- read.csv("data/playback.csv")

playback %>% 
  ggplot() +
  geom_vline(xintercept = range_min) +
  geom_vline(xintercept = range_max) +
  geom_line(aes(x = frequency, y = Leq, group = interaction(tub, treatment), color = treatment)) +
  xlab("Frequency (10 Hz Bins)") +
  ylab("Corrected Amplitude (Leq, dB)") +
  scale_color_manual(values = c("#d95f02", "#1b9e77")) +
  #scale_y_continuous(limits = c(0, 40), breaks = c(seq(0, 40, 5))) +
  theme_classic() +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 12, color = "black"),
        legend.position = "top")

playback %>%  
  filter(! frequency < 20) %>% 
  group_by(treatment, frequency) %>% 
  summarize(mean_leq = mean(leq_test),
            se_leq = plotrix::std.error(leq_test)) %>% 
  ggplot() +
  annotate(geom = "rect", ymin = -95, ymax = -13, xmin = range_min, xmax = range_max, fill = "grey90") +
  geom_vline(xintercept = range_min, linetype = "dashed", color = "#1b9e77") +
  geom_vline(xintercept = range_max, linetype = "dashed", color = "#d95f02") +
  geom_line(aes(x = frequency, y = mean_leq, color = treatment)) +
  geom_ribbon(aes(x = frequency, ymin = mean_leq - se_leq, ymax = mean_leq + se_leq, fill = treatment), alpha = 0.5) +
  xlab("Frequency (10 Hz Bins)") +
  ylab("Amplitude (Leq, dB)\nQuieter <------------> Louder") +
  scale_color_manual("Treatment", values = c("#d95f02", "#1b9e77"),
                     labels = c("Loud", "Quiet")) +
  scale_fill_manual("Treatment", values = c("#d95f02", "#1b9e77"),
                     labels = c("Loud", "Quiet")) +
  scale_y_continuous(limits = c(-95, -13), breaks = c(-90, -75, -60, -45, -30, -15), expand = c(0,0)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family = "sans"),
        axis.title = element_text(size = 14, color = "black", family = "sans"),
        legend.text = element_text(size = 14, color = "black", family = "sans"),
        legend.title = element_text(size = 14, color = "black", family = "sans"),
        legend.position = "top",
        #legend.key.size = unit(1, "cm")
        )
```

**Stimulus**
```{r stimulus_example, echo = FALSE, message = FALSE}
stimulus <- read.csv("data/stimulus.csv") %>% 
  mutate(centered_leq = center_this(Leq_test)) %>% 
  filter(!frequency == 0)

example <- main %>% 
  filter(SpiderID == "ap109", 
         Distance == "close",
         Position == "a",
         Trial == "1")

ggplot() +
  geom_line(aes(x = frequency, y = centered_leq), color = "gold", data = stimulus, size = 2) +
  geom_line(aes(x = Low_Freq, y = centered_leq), color = "purple", data = example, size = 2) +
  xlab("Frequency (10 Hz Bins)") +
  ylab("Relative Amplitude \n(Mean Centered Leq, dB)") +
  scale_y_continuous(limits = c(-10, 30)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family = "sans"),
        axis.title = element_text(size = 14, color = "black", family = "sans"),
        legend.text = element_text(size = 14, color = "black", family = "sans"),
        legend.title = element_text(size = 14, color = "black", family = "sans"),
        legend.position = "top")
```

# Research Questions

## Vibration Transmissiion

**Do webs built by urban and rural spiders under different vibratory conditions differ in the frequency transmission properties?**

```{r close 10hz, echo = FALSE, message = FALSE}
close_ind1 <- main %>% 
  filter(Distance == "close",
         !Site == "Isolated") %>% 
  group_by(SpiderID, Low_Freq, Site, treatment) %>% 
  summarise(mean_leq = mean(centered_leq)) %>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"))

close_ind <- close_ind1 %>% 
  group_by(Low_Freq, Site, treatment) %>% 
  summarize(Leq = mean(mean_leq),
            se = plotrix::std.error(mean_leq))%>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"))

ggplot() +
  annotate(geom = "rect", ymin = -10, ymax = 20, xmin = range_min, xmax = range_max, fill = "grey90") +
  #annotate(geom = "rect", ymin = 0, ymax = 30, xmin = range_min, xmax = range_max, fill = "grey90") +
  geom_vline(xintercept = range_min, linetype = "dashed", color = "#1b9e77") +
  geom_vline(xintercept = range_max, linetype = "dashed", color = "#d95f02") +
  #annotate(geom = "rect", ymin = -1.3, ymax = 2.1, xmin = 0, xmax = 1000, fill = "grey70") +
  #annotate(geom = "rect", ymin = -1.3, ymax = 2.1, xmin = 1000, xmax = 2000, fill = "grey90") +
  geom_line(aes(x = Low_Freq, y = Leq, group = Site, color = Site), data = close_ind) +
  geom_ribbon(aes(x = Low_Freq, ymin = Leq - se, ymax = Leq + se, group = Site, fill = Site), alpha = 0.5, data = close_ind) +
  xlab("Frequency (10 Hz Bins)") +
  ylab("Relative Amplitude \n(Mean Centered Leq, dB)") +
  #ylab("Corrected Amplitude (Leq, dB)") +
  scale_fill_manual("Collection Site", 
                    values = c("#1b9e77", "#d95f02"),
                     labels = c("Rural", "Urban")) +
  scale_color_manual("Collection Site", 
                     values = c("#1b9e77", "#d95f02"),
                     labels = c("Rural", "Urban")) +
  scale_y_continuous(limits = c(-10, 20), breaks = c(-10, 0, 10, 20), expand = c(0,0)) +
  #scale_y_continuous(limits = c(0, 30), breaks = c(0, 10, 20, 30), expand = c(0,0)) +
  scale_x_continuous(limits = c(0, 2100), breaks = c(seq(0, 2000, 500))) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family = "sans"),
        axis.title = element_text(size = 14, color = "black", family = "sans"),
        legend.text = element_text(size = 14, color = "black", family = "sans"),
        legend.title = element_text(size = 14, color = "black", family = "sans"),
        legend.position = "top") +
  facet_wrap(~treatment, labeller = labeller(treatment = treatment.labs)) +
  theme(strip.text = element_text(size = 14, color = "black", family="sans"))
```

```{r far 10hz, echo = FALSE, message = FALSE}
far_ind1 <- main %>% 
  filter(Distance == "far",
         ! Site == "Isolated") %>% 
  group_by(SpiderID, Low_Freq, Site, treatment) %>% 
  summarise(mean_leq = mean(centered_leq))  %>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"))

far_ind <- far_ind1 %>% 
  group_by(Low_Freq, Site, treatment) %>% 
  summarize(Leq = mean(mean_leq),
            se = plotrix::std.error(mean_leq)) %>% 
  mutate(treatment = fct_relevel(treatment, "Quiet", "Loud"))

ggplot() +
  #annotate(geom = "rect", ymin = 0, ymax = 30, xmin = range_min, xmax = range_max, fill = "grey90") +
  annotate(geom = "rect", ymin = -10, ymax = 20, xmin = range_min, xmax = range_max, fill = "grey90") +
  geom_vline(xintercept = range_min, linetype = "dashed", color = "#1b9e77") +
  geom_vline(xintercept = range_max, linetype = "dashed", color = "#d95f02") +
  geom_line(aes(x = Low_Freq, y = Leq, group = Site, color = Site), data = far_ind) +
  geom_ribbon(aes(x = Low_Freq, ymin = Leq - se, ymax = Leq + se, group = Site, fill = Site), alpha = 0.5, data = far_ind) +
  xlab("Frequency (10 Hz Bins)") +
  ylab("Relative Amplitude \n(Mean Centered Leq, dB)") +
  #ylab("Corrected Amplitude (Leq, dB)") +
  scale_fill_manual("Collection Site", 
                    values = c("#1b9e77", "#d95f02"),
                     labels = c("Rural", "Urban")) +
  scale_color_manual("Collection Site", 
                     values = c("#1b9e77", "#d95f02"),
                     labels = c("Rural", "Urban")) +
  scale_y_continuous(limits = c(-10, 20), breaks = c(-10, 0, 10, 20), expand = c(0,0)) +
  #scale_y_continuous(limits = c(0, 30), breaks = c(0, 10, 20, 30), expand = c(0,0)) +
  scale_x_continuous(limits = c(0, 2100), breaks = c(seq(0, 2000, 500))) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family = "sans"),
        axis.title = element_text(size = 14, color = "black", family = "sans"),
        legend.text = element_text(size = 14, color = "black", family = "sans"),
        legend.title = element_text(size = 14, color = "black", family = "sans"),
        legend.position = "top") +
  facet_wrap(~treatment, labeller = labeller(treatment = treatment.labs)) +
  theme(strip.text = element_text(size = 14, color = "black", family="sans"))
```

```{r close 1000 Hz, echo = FALSE, message = FALSE}
close_1000 <- main %>% 
  filter(Distance == "close",
         ! Site == "Isolated") %>% 
  mutate(Freq = ifelse(Low_Freq <= 990, "0-1000", "1000-2000")) %>% 
  mutate(day = mdy(start_date)) %>% 
  group_by(SpiderID, Site, treatment, Freq, day) %>% 
  summarize(mean_leq = mean(centered_leq)) %>% 
  ungroup() %>% 
  #mutate(mean_leq = as.integer(mean_leq)) %>% 
  mutate(Freq = factor(as.character(Freq)),
         Freq = fct_relevel(Freq, "0-1000", "1000-2000")) %>% 
  mutate(treatment = fct_relevel(treatment, "Quiet", "Loud")) 

# raw data
close_1000 %>% 
  group_by(Freq, Site, treatment) %>% 
  summarize(Leq = mean(mean_leq),
            se = plotrix::std.error(mean_leq)) %>% 
  mutate(treatment = fct_relevel(treatment, "Quiet", "Loud")) %>% 
  ggplot() +
  #geom_rect(xmin = as.numeric(close_1000_sum$Freq[[5]]) - 0.5,
  #          xmax = as.numeric(close_1000_sum$Freq[[5]]) + 0.5,
  #          ymin = -0.4, ymax = 0.4, fill = "grey90") +
  #geom_rect(xmin = as.numeric(close_1000_sum$Freq[[1]]) - 0.5,
  #          xmax = as.numeric(close_1000_sum$Freq[[1]]) + 0.5,
  #          ymin = -0.4, ymax = 0.4, fill = "grey70") +
  #annotate(geom = "rect", ymin = -0.4, ymax = 0.4, xmax = "0-1000", xmin = -Inf, fill = "grey70") +
  #annotate(geom = "rect", ymin = -1.3, ymax = 2.1, xmin = 1000, xmax = 2000, fill = "grey90") +
  geom_line(aes(x = Freq, y = Leq, group = Site, color = Site), position = position_dodge(width = 0.25), size = 1) +
  geom_point(aes(x = Freq, y = Leq, group = Site, color = Site), position = position_dodge(width = 0.25), size = 2.5) +
  geom_errorbar(aes(x = Freq, ymin = Leq - se, ymax = Leq + se, group = Site, color = Site), width = 0.25, position = position_dodge(width = 0.25), size = 1) +
  xlab("Frequency (1000 Hz Bins)") +
  ylab("Relative Amplitude (Centered Leq, dB)") +
  #ylab("Corrected Amplitude (Leq, dB)") +
  scale_color_manual("Site", values = c("#1b9e77", "#d95f02")) +
  #scale_y_continuous(limits = c(-0.4, 0.4)) +
  theme_classic() +
  theme(axis.text = element_text(size = 16, color = "black", family = "sans"),
        axis.title = element_text(size = 16, color = "black", family = "sans"),
        legend.text = element_text(size = 16, color = "black", family = "sans"),
        legend.title = element_text(size = 16, color = "black", family = "sans"),
        legend.position = "none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  facet_wrap(~treatment, labeller = labeller(treatment = treatment.labs)) +
  theme(strip.text = element_text(size = 16, color = "black", family="sans"))

shapiro.test(close_1000$mean_leq)
model_close_1000 <- lmer(mean_leq ~ Site * treatment * Freq + (1|SpiderID), data = close_1000)
car::Anova(model_close_1000, type = "II")
emmeans(model_close_1000, pairwise ~ Freq|Site:treatment, adjust = "holm")$contrasts

# non-parametric test
close_1000_rl <- close_1000 %>% 
  filter(Site == "Rural",
         treatment == "Loud")
kruskal.test(mean_leq ~ Freq, data = close_1000_rl)
close_1000_rq <- close_1000 %>% 
  filter(Site == "Rural",
         treatment == "Quiet")
kruskal.test(mean_leq ~ Freq, data = close_1000_rq)
close_1000_ul <- close_1000 %>% 
  filter(Site == "Urban",
         treatment == "Loud")
kruskal.test(mean_leq ~ Freq, data = close_1000_ul)
close_1000_uq <- close_1000 %>% 
  filter(Site == "Urban",
         treatment == "Quiet")
kruskal.test(mean_leq ~ Freq, data = close_1000_uq)

# assumptions
test_close <- augment(model_close_1000, data = close_1000)
resid_close <- ggplot(test_close, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_close$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_close <- ggplot(test_close, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14)) 

cd<-data.frame(cooks.distance(model_close_1000)) 
cd$num <- seq(1, nrow(cd), 1)
colnames(cd) <- c("Cooksd", "Num")
lev<-data.frame(hat(model.matrix(model_close_1000)))
lev$num <- seq(1, nrow(lev), 1)
colnames(lev) <- c("Leverage", "Num")
data_close <- full_join(cd, lev, by = "Num")
lev_close <- data_close %>% 
  pivot_longer(cols = c(Leverage, Cooksd), names_to = "Variable", values_to = "Value") %>% 
  ggplot(aes(x = Num, y = Value, color = Variable)) +
  geom_hline(yintercept = 4/60) +
  geom_point() +
  theme_classic() +
  theme(legend.position = c(0.25, 0.75))

hist_close <- data.frame(ranef = ranef(model_close_1000))
hist_close2 <-hist_close[order(hist_close$ranef.condval),]
ran_ef_close <- hist_close2 %>% 
  ggplot(aes(y = ranef.grp, x = ranef.condval)) +
  geom_point() +
  geom_vline(xintercept = 0) +
  geom_linerange(aes(xmin = ranef.condval - 1.96 * ranef.condsd, xmax = ranef.condval + 1.96 * ranef.condsd)) +
  theme_classic() +
  xlab("Value of the Conditional Mean") +
  ylab("Site")


annotate_figure(ggarrange(resid_close, qq_close, lev_close, ran_ef_close,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2))

# graph predictions
nd = data.frame(expand_grid(Site = levels(factor(close_1000$Site)),
                treatment = levels(factor(close_1000$treatment)),
                Freq = levels(factor(close_1000$Freq))))

nd$fit <- predict(model_close_1000, newdata = nd, se.fit = TRUE, re.form = NA, type = "response")

#bigBoot_close_1000 <- bootMer(model_close_1000, bootStrap, nsim = 1000)
#saveRDS(bigBoot_close_1000, file = "boots/bigBoot_close_1000.Rds")
bigBoot_close_1000 <- readRDS("boots/bigBoot_close_1000.Rds")
predSE <- t(apply(bigBoot_close_1000$t, MARGIN = 2, FUN = sd))
nd$SE <- predSE[1, ]
nd <- nd %>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"))

ggplot() +
  geom_jitter(aes(x = Freq, y = mean_leq, group = Site, color = Site), size = 1, alpha = 0.5, width = 0.1, data = close_1000) +
  geom_line(aes(x = Freq, y = fit, group = Site, color = Site), position = position_dodge(width = 0.25), size = 1, data = nd) +
  geom_point(aes(x = Freq, y = fit, group = Site, color = Site), position = position_dodge(width = 0.25), size = 2.5, data = nd) +
  geom_errorbar(aes(x = Freq, ymin = fit - SE, ymax = fit + SE, group = Site, color = Site), width = 0.25, position = position_dodge(width = 0.25), size = 1, data = nd) +
  xlab("Frequency (1000 Hz Bins)") +
  ylab("Relative Amplitude (Centered Leq, dB)") +
  scale_color_manual("Site", values = c("#1b9e77", "#d95f02")) +
  scale_y_continuous(limits = c(-7, 7), breaks = c(-6, -3, 0, 3, 6)) +
  theme_classic() +
  theme(axis.text = element_text(size = 16, color = "black", family = "sans"),
        axis.title = element_text(size = 16, color = "black", family = "sans"),
        legend.text = element_text(size = 16, color = "black", family = "sans"),
        legend.title = element_text(size = 16, color = "black", family = "sans"),
        legend.position = "none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  facet_wrap(~treatment, labeller = labeller(treatment = treatment.labs)) +
  theme(strip.text = element_text(size = 16, color = "black", family="sans"))
```

```{r far 1000 Hz, echo = FALSE, message = FALSE}
far_1000 <- main %>% 
  filter(Distance == "far",
         ! Site == "Isolated") %>% 
  mutate(Freq = ifelse(Low_Freq <= 990, "0-1000", "1000-2000")) %>% 
  mutate(day = mdy(start_date)) %>% 
  group_by(SpiderID, Site, treatment, Freq, day) %>% 
  summarize(mean_leq = mean(centered_leq)) %>% 
  ungroup() %>% 
  #mutate(mean_leq = as.integer(mean_leq)) %>% 
  mutate(Freq = factor(as.character(Freq)),
         Freq = fct_relevel(Freq, "0-1000", "1000-2000"))

far_1000 %>% 
  group_by(Freq, Site, treatment) %>% 
  summarize(Leq = mean(mean_leq),
            se = plotrix::std.error(mean_leq)) %>% 
  mutate(treatment = fct_relevel(treatment, "Quiet", "Loud")) %>% 
  ggplot() +
  geom_line(aes(x = Freq, y = Leq, group = Site, color = Site), position = position_dodge(width = 0.25), size = 1) +
  geom_point(aes(x = Freq, y = Leq, group = Site, color = Site), position = position_dodge(width = 0.25), size = 2.5) +
  geom_errorbar(aes(x = Freq, ymin = Leq - se, ymax = Leq + se, group = Site, color = Site), width = 0.25, position = position_dodge(width = 0.25), size = 1) +
  xlab("Frequency (1000 Hz Bins)") +
  ylab("Relative Amplitude \n(Centered and Scaled Leq, dB)") +
  scale_color_manual("Site", values = c("#1b9e77", "#d95f02")) +
  #scale_y_continuous(limits = c(-0.4, 0.4)) +
  theme_classic() +
  theme(axis.text = element_text(size = 16, color = "black", family = "sans"),
        axis.title = element_text(size = 16, color = "black", family = "sans"),
        legend.text = element_text(size = 16, color = "black", family = "sans"),
        legend.title = element_text(size = 16, color = "black", family = "sans"),
        legend.position = "none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  facet_wrap(~treatment, labeller = labeller(treatment = treatment.labs)) +
  theme(strip.text = element_text(size = 16, color = "black", family="sans"))

shapiro.test(far_1000$mean_leq)
model_far_1000 <- lmer(mean_leq ~ Site * treatment * Freq + (1|SpiderID), data = far_1000)
car::Anova(model_far_1000)
emmeans(model_far_1000, pairwise ~ Freq|Site,  by = "treatment")$contrasts

# non-parametric test
far_1000_rl <- far_1000 %>% 
  filter(Site == "Rural",
         treatment == "Loud")
kruskal.test(mean_leq ~ Freq, data = far_1000_rl)
far_1000_rq <- far_1000 %>% 
  filter(Site == "Rural",
         treatment == "Quiet")
kruskal.test(mean_leq ~ Freq, data = far_1000_rq)
far_1000_ul <- far_1000 %>% 
  filter(Site == "Urban",
         treatment == "Loud")
kruskal.test(mean_leq ~ Freq, data = far_1000_ul)
far_1000_uq <- far_1000 %>% 
  filter(Site == "Urban",
         treatment == "Quiet")
kruskal.test(mean_leq ~ Freq, data = far_1000_uq)


# assumptions
test_far <- augment(model_far_1000, data = far_1000)
resid_far <- ggplot(test_far, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_far$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_far <- ggplot(test_far, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14)) 

cd<-data.frame(cooks.distance(model_far_1000)) 
cd$num <- seq(1, nrow(cd), 1)
colnames(cd) <- c("Cooksd", "Num")
lev<-data.frame(hat(model.matrix(model_far_1000)))
lev$num <- seq(1, nrow(lev), 1)
colnames(lev) <- c("Leverage", "Num")
data_far <- full_join(cd, lev, by = "Num")
lev_far <- data_far %>% 
  pivot_longer(cols = c(Leverage, Cooksd), names_to = "Variable", values_to = "Value") %>% 
  ggplot(aes(x = Num, y = Value, color = Variable)) +
  geom_hline(yintercept = 4/60) +
  geom_point() +
  theme_classic() +
  theme(legend.position = c(0.25, 0.75))

hist_far <- data.frame(ranef = ranef(model_far_1000))
hist_far2 <-hist_far[order(hist_far$ranef.condval),]
ran_ef_far <- hist_far2 %>% 
  ggplot(aes(y = ranef.grp, x = ranef.condval)) +
  geom_point() +
  geom_vline(xintercept = 0) +
  geom_linerange(aes(xmin = ranef.condval - 1.96 * ranef.condsd, xmax = ranef.condval + 1.96 * ranef.condsd)) +
  theme_classic() +
  xlab("Value of the Conditional Mean") +
  ylab("Site")

annotate_figure(ggarrange(resid_far, qq_far, lev_far, ran_ef_far,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2))

# graph predictions
nd = data.frame(expand_grid(Site = levels(factor(far_1000$Site)),
                treatment = levels(factor(far_1000$treatment)),
                Freq = levels(factor(far_1000$Freq))))

nd$fit <- predict(model_far_1000, newdata = nd, se.fit = TRUE, re.form = NA, type = "response")

#bigBoot_far_1000 <- bootMer(model_far_1000, bootStrap, nsim = 1000)
#saveRDS(bigBoot_far_1000, file = "boots/bigBoot_far_1000.Rds")
bigBoot_far_1000 <- readRDS("boots/bigBoot_far_1000.Rds")
predSE <- t(apply(bigBoot_far_1000$t, MARGIN = 2, FUN = sd))
nd$SE <- predSE[1, ]
nd <- nd %>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"))

ggplot() +
  geom_jitter(aes(x = Freq, y = mean_leq, group = Site, color = Site), size = 1, alpha = 0.5, width = 0.1, data = close_1000) +
  geom_line(aes(x = Freq, y = fit, group = Site, color = Site), position = position_dodge(width = 0.25), size = 1, data = nd) +
  geom_point(aes(x = Freq, y = fit, group = Site, color = Site), position = position_dodge(width = 0.25), size = 2.5, data = nd) +
  geom_errorbar(aes(x = Freq, ymin = fit - SE, ymax = fit + SE, group = Site, color = Site), width = 0.25, position = position_dodge(width = 0.25), size = 1, data = nd) +
  xlab("Frequency (1000 Hz Bins)") +
  ylab("Relative Amplitude (Centered Leq, dB)") +
  scale_color_manual("Site", values = c("#1b9e77", "#d95f02")) +
  scale_y_continuous(limits = c(-7, 7), breaks = c(-6, -3, 0, 3, 6)) +
  theme_classic() +
  theme(axis.text = element_text(size = 16, color = "black", family = "sans"),
        axis.title = element_text(size = 16, color = "black", family = "sans"),
        legend.text = element_text(size = 16, color = "black", family = "sans"),
        legend.title = element_text(size = 16, color = "black", family = "sans"),
        legend.position = "none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  facet_wrap(~treatment, labeller = labeller(treatment = treatment.labs)) +
  theme(strip.text = element_text(size = 16, color = "black", family="sans"))
```

```{r stats_table, echo = FALSE, message = FALSE}
bins_stats <- read.csv(file = "tables/bins_table.csv", header = TRUE) %>% 
  mutate(p_value = factor(p_value),
         p_value = fct_recode(p_value, 
                        "  0.002 **" = "0.002",
                        "< 0.001 ***" = "0.001",
                        "  0.219" = "0.2193",
                        "  0.040 *" = "0.04",
                        "  0.017 *" = "0.017",
                        "  0.330" = "0.33",
                        "  0.015 *" = "0.015")) 

colnames(bins_stats) <- c('Distance', 'Residual DF', 'Collection Site', 'Treatment', '0-1000 Hz \nMean (SE)', '1000-2000 Hz \nMean (SE)',  'Test Statistic', 'P-Value')

flextable(bins_stats[, 1:8]) %>% 
  autofit() %>% 
  merge_v(j = c('Distance', 'Residual DF'), part = "body") %>% 
  theme_vanilla() %>% 
  hline(i = c("1", "2", "3", "5", "6", "7"), 
        j = c("Collection Site", "Treatment", '0-1000 Hz \nMean (SE)', '1000-2000 Hz \nMean (SE)',  'Test Statistic', 'P-Value'), 
        part = "body", 
        border = officer::fp_border(width = 0, color = "black")) %>% 
  bold(bold = TRUE, part = "header") %>% 
  fontsize(size = 10, part = "all") %>% 
  align(align = "left", part = "all") %>%
  valign(valign = "top", part = "all") %>% 
    footnote(i = c(1), j = 1, part = "body", ref_symbols = "a", value = as_paragraph("Results of pairwise comparison following a linear mixed effects model with t-ratio as the test statistic.")) %>%
  footnote(i = c(5), j = 1, ref_symbols = "b", value = as_paragraph("Results of individual Kruskal-Wallis tests following subsetting by collection site and treatment with a chi-squared value as the test statistic.")) #%>% 
  #save_as_image(path = here::here("bins_table.png"))
```

```{r close noise range, Hz, echo = FALSE, message = FALSE}
close_noise <- main %>% 
  filter(Distance == "close",
         ! Site == "Isolated") %>% 
  filter(Low_Freq < range_max & Low_Freq >= range_min) %>% 
  mutate(day = mdy(start_date)) %>% 
  group_by(SpiderID, Site, treatment, day) %>% 
  summarize(mean_leq = mean(centered_leq)) %>% 
  ungroup() %>% 
  mutate(treatment = fct_relevel(treatment, "Quiet", "Loud"))

close_noise %>% 
  group_by(Site, treatment) %>% 
  summarize(Leq = mean(mean_leq),
            se = plotrix::std.error(mean_leq)) %>% 
  mutate(treatment = fct_relevel(treatment, "Quiet", "Loud")) %>% 
  ggplot() +
  #geom_rect(xmin = as.numeric(close_1000_sum$Freq[[5]]) - 0.5,
  #          xmax = as.numeric(close_1000_sum$Freq[[5]]) + 0.5,
  #          ymin = -0.4, ymax = 0.4, fill = "grey90") +
  #geom_rect(xmin = as.numeric(close_1000_sum$Freq[[1]]) - 0.5,
  #          xmax = as.numeric(close_1000_sum$Freq[[1]]) + 0.5,
  #          ymin = -0.4, ymax = 0.4, fill = "grey70") +
  #annotate(geom = "rect", ymin = -0.4, ymax = 0.4, xmax = "0-1000", xmin = -Inf, fill = "grey70") +
  #annotate(geom = "rect", ymin = -1.3, ymax = 2.1, xmin = 1000, xmax = 2000, fill = "grey90") +
  geom_line(aes(x = treatment, y = Leq, group = Site, color = Site), position = position_dodge(width = 0.25), size = 1) +
  geom_point(aes(x = treatment, y = Leq, group = Site, color = Site), position = position_dodge(width = 0.25), size = 2.5) +
  geom_errorbar(aes(x = treatment, ymin = Leq - se, ymax = Leq + se, group = Site, color = Site), width = 0.25, position = position_dodge(width = 0.25), size = 1) +
  xlab("Treatment") +
  ylab("Relative Amplitude (Centered Leq, dB)") +
  scale_color_manual("Site", values = c("#1b9e77", "#d95f02")) +
  #scale_y_continuous(limits = c(-0.4, 0.4)) +
  theme_classic() +
  theme(axis.text = element_text(size = 16, color = "black", family = "sans"),
        axis.title = element_text(size = 16, color = "black", family = "sans"),
        legend.text = element_text(size = 16, color = "black", family = "sans"),
        legend.title = element_text(size = 16, color = "black", family = "sans"),
        legend.position = "top") 

shapiro.test(close_noise$mean_leq)
model_close_noise <- lm(mean_leq ~ Site * treatment, data = close_noise)
car::Anova(model_close_noise)
emmeans(model_close_noise, pairwise ~ Site,  by = "treatment")$contrasts
emmeans(model_close_noise, pairwise ~ treatment,  by = "Site")$contrasts

nd = data.frame(expand_grid(Site = levels(factor(close_noise$Site)),
                treatment = levels(factor(close_noise$treatment))))

nd$fit <- predict(model_close_noise, newdata = nd, se.fit = TRUE, re.form = NA, type = "response")$fit
nd$SE <- predict(model_close_noise, newdata = nd, se.fit = TRUE, re.form = NA, type = "response")$se.fit
nd <- nd %>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"))

ggplot() +
    annotate(geom = "rect", ymin = -10, ymax = 15, xmin = -Inf, xmax = Inf, fill = "grey90") +
  geom_jitter(aes(x = treatment, y = mean_leq, group = Site, color = Site), size = 1, alpha = 0.5, width = 0.1, data = close_noise) +
  geom_line(aes(x = treatment, y = fit, group = Site, color = Site), position = position_dodge(width = 0.25), size = 1, data = nd) +
  geom_point(aes(x = treatment, y = fit, group = Site, color = Site), position = position_dodge(width = 0.25), size = 1.5, data = nd) +
  geom_errorbar(aes(x = treatment, ymin = fit - SE, ymax = fit + SE, group = Site, color = Site), width = 0.25, position = position_dodge(width = 0.25), size = 1, data = nd) +
  xlab("Treatment (4 Days)") +
  ylab("Relative Amplitude \n(Mean Centered Leq, dB)") +
  scale_color_manual("Collection Site", values = c("#1b9e77", "#d95f02")) +
  scale_y_continuous(limits = c(-10, 15), breaks = c(-10, -5, 0, 5, 10, 15), expand = c(0,0)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family = "sans"),
        axis.title = element_text(size = 14, color = "black", family = "sans"),
        legend.text = element_text(size = 14, color = "black", family = "sans"),
        legend.title = element_text(size = 14, color = "black", family = "sans"),
        legend.position = "none") 
```

```{r far noise range, Hz, echo = FALSE, message = FALSE}
far_noise <- main %>% 
  filter(Distance == "far",
         ! Site == "Isolated") %>% 
  filter(Low_Freq < range_max & Low_Freq >= range_min) %>% 
  mutate(day = mdy(start_date)) %>% 
  group_by(SpiderID, Site, treatment, day) %>% 
  summarize(mean_leq = mean(centered_leq)) %>% 
  ungroup() %>% 
  mutate(treatment = fct_relevel(treatment, "Quiet", "Loud"))

far_noise %>% 
  group_by(Site, treatment) %>% 
  summarize(Leq = mean(mean_leq),
            se = plotrix::std.error(mean_leq)) %>% 
  mutate(treatment = fct_relevel(treatment, "Quiet", "Loud")) %>% 
  ggplot() +
  #geom_rect(xmin = as.numeric(close_1000_sum$Freq[[5]]) - 0.5,
  #          xmax = as.numeric(close_1000_sum$Freq[[5]]) + 0.5,
  #          ymin = -0.4, ymax = 0.4, fill = "grey90") +
  #geom_rect(xmin = as.numeric(close_1000_sum$Freq[[1]]) - 0.5,
  #          xmax = as.numeric(close_1000_sum$Freq[[1]]) + 0.5,
  #          ymin = -0.4, ymax = 0.4, fill = "grey70") +
  #annotate(geom = "rect", ymin = -0.4, ymax = 0.4, xmax = "0-1000", xmin = -Inf, fill = "grey70") +
  #annotate(geom = "rect", ymin = -1.3, ymax = 2.1, xmin = 1000, xmax = 2000, fill = "grey90") +
  geom_line(aes(x = treatment, y = Leq, group = Site, color = Site), position = position_dodge(width = 0.25), size = 1) +
  geom_point(aes(x = treatment, y = Leq, group = Site, color = Site), position = position_dodge(width = 0.25), size = 2.5) +
  geom_errorbar(aes(x = treatment, ymin = Leq - se, ymax = Leq + se, group = Site, color = Site), width = 0.25, position = position_dodge(width = 0.25), size = 1) +
  xlab("Treatment") +
  ylab("Relative Amplitude \n(Centered Leq, dB)") +
  scale_color_manual("Site", values = c("#1b9e77", "#d95f02")) +
  #scale_y_continuous(limits = c(-0.4, 0.4)) +
  theme_classic() +
  theme(axis.text = element_text(size = 16, color = "black", family = "sans"),
        axis.title = element_text(size = 16, color = "black", family = "sans"),
        legend.text = element_text(size = 16, color = "black", family = "sans"),
        legend.title = element_text(size = 16, color = "black", family = "sans"),
        legend.position = "top") 

shapiro.test(far_noise$mean_leq) # not normal
#model_far_noise <- lm(mean_leq ~ Site * treatment, data = far_noise)
#car::Anova(model_far_noise)
#emmeans(model_far_noise, pairwise ~ Site,  by = "treatment")$contrasts
#emmeans(model_far_noise, pairwise ~ treatment,  by = "Site")$contrasts

#nd = data.frame(expand_grid(Site = levels(factor(close_noise$Site)),
#                treatment = levels(factor(close_noise$treatment))))

#nd$fit <- predict(model_far_noise, newdata = nd, se.fit = TRUE, re.form = NA, type = "response")$fit
#nd$SE <- predict(model_far_noise, newdata = nd, se.fit = TRUE, re.form = NA, type = "response")$se.fit
#nd <- nd %>% 
#  mutate(treatment = factor(treatment),
#         treatment = fct_relevel(treatment, "Quiet", "Loud"))

#ggplot() +
#      annotate(geom = "rect", ymin = -10, ymax = 15, xmin = -Inf, xmax #= Inf, fill = "grey90") +
#  geom_jitter(aes(x = treatment, y = mean_leq, group = Site, color = #Site), size = 1, alpha = 0.5, width = 0.1, data = far_noise) +
#  geom_line(aes(x = treatment, y = fit, group = Site, color = Site), #position = position_dodge(width = 0.25), size = 1, data = nd) +
#  geom_point(aes(x = treatment, y = fit, group = Site, color = Site), #position = position_dodge(width = 0.25), size = 2.5, data = nd) +
#  geom_errorbar(aes(x = treatment, ymin = fit - SE, ymax = fit + SE, #group = Site, color = Site), width = 0.25, position = #position_dodge(width = 0.25), size = 1, data = nd) +
#  xlab("Treatment (4 Days)") +
#  ylab("Relative Amplitude \n(Mean Centered Leq, dB)") +
#  scale_color_manual("Collection Site", values = c("#1b9e77", #"#d95f02")) +
#  scale_y_continuous(limits = c(-10, 15), breaks = c(-10, -5, 0, 5, #10, 15), expand = c(0,0)) +
#  theme_classic() +
#  theme(axis.text = element_text(size = 14, color = "black", family = #"sans"),
#        axis.title = element_text(size = 14, color = "black", family = #"sans"),
#        legend.text = element_text(size = 14, color = "black", family #= "sans"),
#        legend.title = element_text(size = 14, color = "black", family #= "sans"),
#        legend.position = "none") 


far_noise_l <- far_noise %>% 
  filter(treatment == "Loud")
kruskal.test(mean_leq ~ Site, data = far_noise_l)

far_noise_q <- far_noise %>% 
  filter(treatment == "Quiet")
kruskal.test(mean_leq ~ Site, data = far_noise_q)

far_noise_u <- far_noise %>% 
  filter(Site == "Urban")
kruskal.test(mean_leq ~ treatment, data = far_noise_u)

far_noise_r <- far_noise %>% 
  filter(Site == "Rural")
kruskal.test(mean_leq ~ treatment, data = far_noise_r)

far_noise_sum <- far_noise %>% 
  group_by(Site, treatment) %>% 
  summarize(mean = mean(mean_leq),
            se = plotrix::std.error(mean_leq))

ggplot() +
      annotate(geom = "rect", ymin = -10, ymax = 15, xmin = -Inf, xmax = Inf, fill = "grey90") +
  geom_jitter(aes(x = treatment, y = mean_leq, group = Site, color = Site), size = 1, alpha = 0.5, width = 0.1, data = far_noise) +
  geom_line(aes(x = treatment, y = mean, group = Site, color = Site), position = position_dodge(width = 0.25), size = 1, data = far_noise_sum) +
  geom_point(aes(x = treatment, y = mean, group = Site, color = Site), position = position_dodge(width = 0.25), size = 1.5, data = far_noise_sum) +
  geom_errorbar(aes(x = treatment, ymin = mean - se, ymax = mean + se, group = Site, color = Site), width = 0.25, position = position_dodge(width = 0.25), size = 1, data = far_noise_sum) +
  xlab("Treatment (4 Days)") +
  ylab("Relative Amplitude \n(Mean Centered Leq, dB)") +
  scale_color_manual("Collection Site", values = c("#1b9e77", "#d95f02")) +
  scale_y_continuous(limits = c(-10, 15), breaks = c(-10, -5, 0, 5, 10, 15), expand = c(0,0)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family = "sans"),
        axis.title = element_text(size = 14, color = "black", family = "sans"),
        legend.text = element_text(size = 14, color = "black", family = "sans"),
        legend.title = element_text(size = 14, color = "black", family = "sans"),
        legend.position = "none") 
```

*Isolated*

```{r close 10hz isolated, echo = FALSE, message = FALSE}
close_indi1 <- main %>% 
  filter(Distance == "close") %>% 
  group_by(SpiderID, Low_Freq, Site, treatment) %>% 
  summarise(mean_leq = mean(centered_leq)) %>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"))

close_indi <- close_indi1 %>% 
  group_by(Low_Freq, Site, treatment) %>% 
  summarize(Leq = mean(mean_leq),
            se = plotrix::std.error(mean_leq))%>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"))

ggplot() +
  annotate(geom = "rect", ymin = -10, ymax = 20, xmin = 360, xmax = 610, fill = "grey90") +
  #annotate(geom = "rect", ymin = 0, ymax = 30, xmin = 360, xmax = 610, fill = "grey90") +
  geom_vline(xintercept = 360, linetype = "dashed", color = "#1b9e77") +
  geom_vline(xintercept = 610, linetype = "dashed", color = "#d95f02") +
  #annotate(geom = "rect", ymin = -1.3, ymax = 2.1, xmin = 0, xmax = 1000, fill = "grey70") +
  #annotate(geom = "rect", ymin = -1.3, ymax = 2.1, xmin = 1000, xmax = 2000, fill = "grey90") +
  geom_line(aes(x = Low_Freq, y = Leq, group = Site, color = Site), data = close_indi) +
  geom_ribbon(aes(x = Low_Freq, ymin = Leq - se, ymax = Leq + se, group = Site, fill = Site), alpha = 0.5, data = close_indi) +
  xlab("Frequency (10 Hz Bins)") +
  ylab("Relative Amplitude (Centered Leq, dB)") +
  #ylab("Corrected Amplitude (Leq, dB)") +
  scale_fill_manual("Collection Site", 
                    values = c("#7570b3", "#1b9e77", "#d95f02"),
                     labels = c("Isolated", "Rural", "Urban")) +
  scale_color_manual("Collection Site", 
                     values = c("#7570b3", "#1b9e77", "#d95f02"),
                     labels = c("Isolated", "Rural", "Urban")) +
  scale_y_continuous(limits = c(-10, 20), breaks = c(-10, 0, 10, 20), expand = c(0,0)) +
  #scale_y_continuous(limits = c(0, 30), breaks = c(0, 10, 20, 30), expand = c(0,0)) +
  scale_x_continuous(limits = c(0, 2100), breaks = c(seq(0, 2000, 500))) +
  theme_classic() +
  theme(axis.text = element_text(size = 16, color = "black", family = "sans"),
        axis.title = element_text(size = 16, color = "black", family = "sans"),
        legend.text = element_text(size = 16, color = "black", family = "sans"),
        legend.title = element_text(size = 16, color = "black", family = "sans"),
        legend.position = "top") +
  facet_wrap(~treatment, labeller = labeller(treatment = treatment.labs)) +
  theme(strip.text = element_text(size = 16, color = "black", family="sans"))
```

```{r far 10hz isolated, echo = FALSE, message = FALSE}
far_indi1 <- main %>% 
  filter(Distance == "far") %>% 
  group_by(SpiderID, Low_Freq, Site, treatment) %>% 
  summarise(mean_leq = mean(centered_leq))  %>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"))

far_indi <- far_indi1 %>% 
  group_by(Low_Freq, Site, treatment) %>% 
  summarize(Leq = mean(mean_leq),
            se = plotrix::std.error(mean_leq)) %>% 
  mutate(treatment = fct_relevel(treatment, "Quiet", "Loud"))

ggplot() +
  annotate(geom = "rect", ymin = -10, ymax = 20, xmin = 360, xmax = 610, fill = "grey90") +
  geom_vline(xintercept = 360, linetype = "dashed", color = "#1b9e77") +
  geom_vline(xintercept = 610, linetype = "dashed", color = "#d95f02") +
  geom_line(aes(x = Low_Freq, y = Leq, group = Site, color = Site), data = far_indi) +
  geom_ribbon(aes(x = Low_Freq, ymin = Leq - se, ymax = Leq + se, group = Site, fill = Site), alpha = 0.5, data = far_indi) +
  xlab("Frequency (10 Hz Bins)") +
  ylab("Relative Amplitude (Centered Leq, dB)") +
  scale_fill_manual("Collection Site", 
                    values = c("#7570b3", "#1b9e77", "#d95f02"),
                     labels = c("Isolated", "Rural", "Urban")) +
  scale_color_manual("Collection Site", 
                     values = c("#7570b3", "#1b9e77", "#d95f02"),
                     labels = c("Isolated", "Rural", "Urban")) +
  scale_y_continuous(limits = c(-10, 20), breaks = c(-10, 0, 10, 20), expand = c(0,0)) +
  scale_x_continuous(limits = c(0, 2100), breaks = c(seq(0, 2000, 500))) +
  theme_classic() +
  theme(axis.text = element_text(size = 16, color = "black", family = "sans"),
        axis.title = element_text(size = 16, color = "black", family = "sans"),
        legend.text = element_text(size = 16, color = "black", family = "sans"),
        legend.title = element_text(size = 16, color = "black", family = "sans"),
        legend.position = "top") +
  facet_wrap(~treatment, labeller = labeller(treatment = treatment.labs)) +
  theme(strip.text = element_text(size = 16, color = "black", family="sans"))
```

## Frequency Response 

**Do spiders shift their response to frequencies based on experience with different vibratory conditions?**

**2022** - Deciding to pool rural but not urban (campus only)

```{r 2022 all responses, echo = FALSE, message = FALSE}
all_2022 <- freq_response_all %>% 
  filter(Year == 2022)

# sample size at four locations
all_2022%>% 
  group_by(Location) %>% 
  count() # divide by 10

all_2022_location <- all_2022 %>% 
  mutate(frequency = as.character(frequency),
         frequency = as.numeric(frequency)) %>% 
  group_by(Location, Site, frequency) %>% 
  summarize(reactions = sum(react),
            prop = ifelse(Location == "Campus", reactions/23,
                          ifelse(Location == "Corman", reactions/12,
                                 ifelse(Location == "Herman", reactions/20, reactions/12)))) %>% 
  unique() %>% 
  mutate(Location = factor(Location), 
         Location = fct_recode(Location, "Urban_1" = "Campus", "Urban_2" = "Corman", "Rural_1" = "Pope", "Rural_2" = "Herman"),
         Location = fct_relevel(Location, "Rural_1", "Rural_2", "Urban_1", "Urban_2"))

# sample size urban vs rural
all_2022 %>% 
  group_by(Site) %>% 
  count() # divide by 10

all_2022_site <- all_2022 %>% 
  mutate(frequency = as.character(frequency),
         frequency = as.numeric(frequency)) %>% 
  group_by(Site, frequency) %>% 
  summarize(reactions = sum(react),
            prop = ifelse(Site == "Urban", reactions/35, reactions/32)) %>% 
  unique()

all <- ggplot() +
  geom_line(aes(x = frequency, y = prop, group = Location, color = Location), data = all_2022_location, linewidth = 1) +
    #geom_line(aes(x = frequency, y = prop), data = all_2022_site, color = "black", linewidth = 1) +
  xlab("Frequency (100 Hz Bins)") +
  ylab("Proportion of Reacting Spiders") +
  scale_y_continuous(limits = c(0, 1), breaks = c(seq(0, 1, 0.2))) +
  scale_x_continuous(limits = c(0, 1000), breaks = c(seq(0, 1000, 250))) +
  scale_color_manual("Locations", 
                     values = c("#1b9e77", "#74e7c5", "#d95f02", "#fead6f"),
                     labels = c("Rural 1", "Rural 2", "Urban 1", "Urban 2")) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family="sans"),
        axis.title = element_text(size = 14, color = "black", family="sans"),
        legend.text = element_text(size = 14, color = "black", family="sans"),
        legend.title = element_text(size = 14, color = "black", family="sans"),
        legend.position = "top",
        strip.text = element_text(size = 14, color = "black", family="sans")) +
  facet_wrap(~Site) +
  ggtitle("All Responses")
```

```{r 2022 attacks only, echo = FALSE, message = FALSE}
attack_2022 <- freq_response_attack %>% 
  filter(Year == 2022) 

# sample size by four locations
freq_response_attack %>% 
  filter(Year == 2022) %>% 
  group_by(Location) %>% 
  count() # divide by 10

attack_2022_location <- attack_2022 %>% 
  mutate(frequency = as.character(frequency),
         frequency = as.numeric(frequency)) %>% 
  group_by(Location, Site, frequency) %>% 
  summarize(reactions = sum(react),
            prop = ifelse(Location == "Campus", reactions/19,
                          ifelse(Location == "Corman", reactions/11,
                                 ifelse(Location == "Herman", reactions/20, reactions/10)))) %>% 
  unique() %>% 
  mutate(Location = factor(Location), 
         Location = fct_recode(Location, "Urban_1" = "Campus", "Urban_2" = "Corman", "Rural_1" = "Pope", "Rural_2" = "Herman"),
         Location = fct_relevel(Location, "Rural_1", "Rural_2", "Urban_1", "Urban_2"))

# sample size for sites urban vs rural
attack_2022 %>% 
  group_by(Site) %>% 
  count() # divide by 10

attack_2022_site <- attack_2022 %>% 
  mutate(frequency = as.character(frequency),
         frequency = as.numeric(frequency)) %>% 
  group_by(Site, frequency) %>% 
  summarize(reactions = sum(react),
            prop = ifelse(Site == "Urban", reactions/30, reactions/30)) %>% 
  unique()

attacks <- ggplot() +
  geom_line(aes(x = frequency, y = prop, group = Location, color = Location), data = attack_2022_location, linewidth = 1) +
    #geom_line(aes(x = frequency, y = prop), data = attack_2022_site, color = "black", linewidth = 1) +
  xlab("Frequency (100 Hz Bins)") +
  ylab("Proportion of Attacking Spiders") +
  scale_y_continuous(limits = c(0, 1), breaks = c(seq(0, 1, 0.2))) +
  scale_x_continuous(limits = c(0, 1000), breaks = c(seq(0, 1000, 250))) +
  scale_color_manual("Locations", 
                     values = c("#1b9e77", "#74e7c5", "#d95f02", "#fead6f"),
                     labels = c("Rural 1", "Rural 2", "Urban 1", "Urban 2")) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family = "sans"),
        axis.title = element_text(size = 14, color = "black", family = "sans"),
        legend.text = element_text(size = 14, color = "black", family = "sans"),
        legend.title = element_text(size = 14, color = "black", family = "sans"),
        legend.position = "top",
        strip.text = element_text(size = 14, color = "black", family="sans")) +
  facet_wrap(~Site) +
  ggtitle("Attacks Only")

ggarrange(all, attacks, nrow = 2)
```

**Frequency Response**

```{r all frequency response, echo = FALSE, message = FALSE}
fr_all <- freq_response_all %>% 
  filter(! Location == "Corman") %>% 
  mutate(Group = ifelse(Year == 2022, "2022",
                        ifelse(Year == 2023 & treatment == "Loud", "2023_Loud", "2023_Quiet")),
         Group = factor(Group),
         Group = fct_relevel(Group, "2022", "2023_Quiet", "2023_Loud")) %>% 
  dplyr::select(SpiderID, Group, Site, frequency, react)

# sample sizes
fr_all %>% 
  group_by(Group, Site) %>% 
  count() # divide by 10

fr_all_props <- fr_all%>% 
  group_by(Group, Site, frequency) %>% 
  summarize(reactions = sum(react), 
            prop = ifelse(Group == "2022" & Site == "Rural", reactions/32,
                   ifelse(Group == "2022" & Site == "Urban", reactions/23,
                   ifelse(Group == "2023_Quiet" & Site == "Rural", reactions/12, 
                   ifelse(Group == "2023_Quiet" & Site == "Urban", reactions/14,
                   ifelse(Group == "2023_Loud" & Site == "Rural", reactions/10, reactions/13)))))) %>% 
  ungroup() %>% 
  unique() %>% 
  mutate(frequency = as.character(frequency),
         frequency = as.numeric(frequency),
         Group = fct_recode(Group, "Baseline (2022)" = "2022", "After Quiet Treatment" = "2023_Quiet", "After Loud Treatment" = "2023_Loud"),
         Group = fct_relevel(Group, "Baseline (2022)", "After Quiet Treatment", "After Loud Treatment"),
         Site = fct_relevel(Site, "Rural", "Urban"))

fr_all_props %>% 
  ggplot() +
  geom_tile(aes(x = Group, y = frequency, fill = Site, alpha = prop), linewidth = 2, width = 0.9) +
  scale_fill_manual(name = "Collection Site", values = c("#1b9e77", "#d95f02")) +
  scale_alpha_continuous(name = "Prop. Reacted", range = c(0, 1), limits = c(0, 0.6), breaks = c(0, 0.1, 0.2, 0.3, 0.35, 0.4, 0.5)) +
  xlab("") +
  ylab("Pure Tone Frequency (100 Hz Increments)") +
  scale_y_continuous(breaks = c(0, 200, 400, 600, 800, 1000)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family="sans"),
        axis.title = element_text(size = 14, color = "black", family="sans"),
        legend.text = element_text(size = 14, color = "black", family="sans"),
        legend.title = element_text(size = 14, color = "black", family="sans"),
        legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
        strip.text = element_text(size = 14, color = "black", family="sans")) +
  facet_wrap(~Site) 

# above 35%
#Rural
# Baseline (2022) 400, 500, 800, 200
# After Quiet 400, 1000, 700
# After Loud 400, 300, 600

#Urban
# Baseline (2022) 500, 200, 400, 600, 700, 800
# After Quiet 200, 300, 400, 800, 600
# After Loud 300, 800, 100, 400

# presentation
fr_all_props %>% 
  ggplot() +
  geom_tile(aes(x = Group, y = frequency, fill = prop), color ="white", linewidth = 2, width = 0.9) +
  scale_fill_gradient("Prop. Attacks", low="grey30", high="grey30", na.value = "white", limits = c(0.4, 0.6), breaks = c(0.4, 0.6)) +
  xlab("") +
  ylab("Pure Tone Frequency (100 Hz Increments)") +
  scale_y_continuous(breaks = c(0, 200, 400, 600, 800, 1000)) +
  theme_classic() +
  theme(axis.text = element_text(size = 16, color = "black", family="sans"),
        axis.title = element_text(size = 16, color = "black", family="sans"),
        legend.text = element_text(size = 16, color = "black", family="sans"),
        legend.title = element_text(size = 16, color = "black", family="sans"),
        legend.position = "none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), 
        strip.text = element_text(size = 16, color = "black", family="sans")) +
  facet_wrap(~Site) 
```

```{r attacks frequency response, echo = FALSE, message = FALSE}
fr_attack <- freq_response_attack %>% 
  filter(! Location == "Corman") %>% 
  mutate(Group = ifelse(Year == 2022, "2022",
                        ifelse(Year == 2023 & treatment == "Loud", "2023_Loud", "2023_Quiet")),
         Group = factor(Group),
         Group = fct_relevel(Group, "2022", "2023_Quiet", "2023_Loud")) %>% 
  dplyr::select(SpiderID, Group, Site, frequency, react)

# sample sizes
fr_attack %>% 
  group_by(Group, Site) %>% 
  count() # divide by 10

fr_attack_prop <- fr_attack%>% 
  group_by(Group, Site, frequency) %>% 
  summarize(reactions = sum(react), 
            prop = ifelse(Group == "2022" & Site == "Rural", reactions/30,
                   ifelse(Group == "2022" & Site == "Urban", reactions/19,
                   ifelse(Group == "2023_Quiet" & Site == "Rural", reactions/7, 
                   ifelse(Group == "2023_Quiet" & Site == "Urban", reactions/12,
                   ifelse(Group == "2023_Loud" & Site == "Rural", reactions/6, reactions/10)))))) %>% 
  ungroup() %>% 
  unique() %>% 
  mutate(frequency = as.character(frequency),
         frequency = as.numeric(frequency),
         Group = fct_recode(Group, "Baseline (2022)" = "2022", "After Quiet Treatment" = "2023_Quiet", "After Loud Treatment" = "2023_Loud"),
         Group = fct_relevel(Group, "Baseline (2022)", "After Quiet Treatment", "After Loud Treatment"),
         Site = fct_relevel(Site, "Rural", "Urban"))

fr_attack_prop %>% 
  ggplot() +
    #annotate(geom = "rect", ymin = 450, ymax = 650, xmin = -Inf, xmax = Inf, fill = "grey90") +
  geom_tile(aes(x = Group, y = frequency, fill = Site, alpha = prop), linewidth = 2, width = 0.9) +
  scale_alpha_continuous(name = "Prop. Attacked", range = c(0, 1), limits = c(0, 0.6), breaks = c(0, 0.1, 0.2, 0.3, 0.35, 0.4, 0.5)) +
  scale_fill_manual(name = "Collection Site", values = c("#1b9e77", "#d95f02")) +
  xlab("") +
  ylab("Pure Tone Frequency (100 Hz Increments)") +
  scale_y_continuous(breaks = c(0, 200, 400, 600, 800, 1000)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family="sans"),
        axis.title = element_text(size = 14, color = "black", family="sans"),
        legend.text = element_text(size = 14, color = "black", family="sans"),
        legend.title = element_text(size = 14, color = "black", family="sans"),
        legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
        strip.text = element_text(size = 14, color = "black", family="sans")) +
  facet_wrap(~Site) 

# above 35%
#Rural
# Baseline (2022) 500, 800
# After Quiet 300, 400
# After Loud 400, 500, 600

#Urban
# Baseline (2022) 500, 800, 400
# After Quiet 200, 600
# After Loud 800

# presentation
fr_attack_prop %>% 
  ggplot() +
  geom_tile(aes(x = Group, y = frequency, fill = prop), color ="white", linewidth = 2, width = 0.9) +
  scale_fill_gradient("Prop. Attacks", low="grey30", high="grey30", na.value = "white", limits = c(0.4, 0.6), breaks = c(0.4, 0.6)) +
  xlab("") +
  ylab("Pure Tone Frequency (100 Hz Increments)") +
  scale_y_continuous(breaks = c(0, 200, 400, 600, 800, 1000)) +
  theme_classic() +
  theme(axis.text = element_text(size = 16, color = "black", family="sans"),
        axis.title = element_text(size = 16, color = "black", family="sans"),
        legend.text = element_text(size = 16, color = "black", family="sans"),
        legend.title = element_text(size = 16, color = "black", family="sans"),
        legend.position = "none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), 
        strip.text = element_text(size = 16, color = "black", family="sans")) +
  facet_wrap(~Site) 
```

```{r attacks across age, echo = FALSE, message = FALSE}
age <- freq_response_attack %>% 
  filter(Year == 2023) %>% 
  unite("site_treatment", c(Site, treatment), sep = "_", remove = FALSE) %>% 
  mutate(frequency = fct_recode(frequency, "1000 Hz" = "1000", "900 Hz" = "900", "800 Hz" = "800", "700 Hz" = "700", "600 Hz" = "600", "500 Hz" = "500", "400 Hz" = "400", "300 Hz" = "300", "200 Hz" = "200", "100 Hz" = "100"), frequency = fct_relevel(frequency, "1000 Hz", "900 Hz", "800 Hz", "700 Hz", "600 Hz", "500 Hz", "400 Hz", "300 Hz", "200 Hz", "100 Hz"),
         treatment = fct_relevel(treatment, "Quiet", "Loud"))

age %>% 
  ggplot() +
  #geom_point(aes(x = Rest_Days, y = react), color = "black", size = 0.5) +
  stat_smooth(aes(x = Rest_Days, y = react), color = "black", method="glm", se=FALSE, method.args = list(family=binomial)) +
  ylab("Spider Attacked") + 
  xlab("Number of Days Since Playback") +
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1)) +
  theme_classic() +
  theme(axis.text = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 10, color = "black"),
        strip.text = element_text(size = 7, color = "black"),
        legend.position = "none") +
  facet_grid(frequency ~ Site + treatment)
```

**Isolated Frequency Responses**

```{r isolated all, echo = FALSE, message = FALSE}
# sample sizes
isolated_all %>% 
  group_by(before_after, treatment) %>% 
  count() # divide by 10

is_all <- isolated_all%>% 
  group_by(before_after, treatment, frequency) %>% 
  summarize(reactions = sum(react), 
            prop = ifelse(before_after == "After" & treatment == "Loud", reactions/6,
                   ifelse(before_after == "After" & treatment == "Quiet", reactions/4,
                   ifelse(before_after == "Before" & treatment == "Loud", reactions/10, reactions/10)))) %>% 
  ungroup() %>% 
  unique() %>% 
  mutate(frequency = as.character(frequency),
         frequency = as.numeric(frequency),
         treatment = fct_relevel(treatment, "Quiet", "Loud"),
         before_after = fct_relevel(before_after, "Before", "After"))

is_all %>% 
  ggplot() +
  geom_tile(aes(x = before_after, y = frequency, fill = treatment, alpha = prop), linewidth = 2, width = 0.9) +
  scale_fill_manual(name = "Treatment", values = c("#1b9e77", "#d95f02")) +
  scale_alpha_continuous(name = "Prop. Reacted", range = c(0, 1), limits = c(0, 0.6), breaks = c(0, 0.1, 0.2, 0.3, 0.33, 0.4, 0.5)) +
  xlab("") +
  ylab("Pure Tone Frequency (100 Hz Increments)") +
  scale_y_continuous(breaks = c(0, 200, 400, 600, 800, 1000)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family="sans"),
        axis.title = element_text(size = 14, color = "black", family="sans"),
        legend.text = element_text(size = 14, color = "black", family="sans"),
        legend.title = element_text(size = 14, color = "black", family="sans"),
        legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
        strip.text = element_text(size = 14, color = "black", family="sans")) +
  facet_wrap(~treatment) 

# above 33%
#Quiet
# Before 400, 1000, 200, 700
# After 300, 600

#Loud
# Before 600, 200, 900
# After 900, 400, 500, 600, 700
```

```{r isolated attack, echo = FALSE, message = FALSE}
# sample sizes
isolated_attack %>% 
  group_by(before_after, treatment) %>% 
  count() # divide by 10

is_attacks <- isolated_attack %>% 
  group_by(before_after, treatment, frequency) %>% 
  summarize(reactions = sum(react), 
            prop = ifelse(before_after == "After" & treatment == "Loud", reactions/5,
                   ifelse(before_after == "After" & treatment == "Quiet", reactions/3,
                   ifelse(before_after == "Before" & treatment == "Loud", reactions/8, reactions/9)))) %>% 
  ungroup() %>% 
  unique() %>% 
  mutate(frequency = as.character(frequency),
         frequency = as.numeric(frequency),
         treatment = fct_relevel(treatment, "Quiet", "Loud"),
         before_after = fct_relevel(before_after, "Before", "After"))

is_attacks %>% 
  ggplot() +
  geom_tile(aes(x = before_after, y = frequency, fill = treatment, alpha = prop), linewidth = 2, width = 0.9) +
  scale_fill_manual(name = "Treatment", values = c("#1b9e77", "#d95f02")) +
  scale_alpha_continuous(name = "Prop. Attacked", range = c(0, 1), limits = c(0, 0.6), breaks = c(0, 0.1, 0.2, 0.3, 0.33, 0.4, 0.5)) +
  xlab("") +
  ylab("Pure Tone Frequency (100 Hz Increments)") +
  scale_y_continuous(breaks = c(0, 200, 400, 600, 800, 1000)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family="sans"),
        axis.title = element_text(size = 14, color = "black", family="sans"),
        legend.text = element_text(size = 14, color = "black", family="sans"),
        legend.title = element_text(size = 14, color = "black", family="sans"),
        legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
        strip.text = element_text(size = 14, color = "black", family="sans")) +
  facet_wrap(~treatment) 

# above 33%
#Quiet
# Before 200, 400, 700
# After 300, 500, 600

#Loud
# Before 900, 500
# After 400, 500, 600, 900
```

**Silk Mass**

```{r silk_mass, echo = FALSE, message = FALSE}
silk <- main %>% 
  ungroup() %>% 
  filter(! Site == "Isolated") %>% 
  dplyr::select(SpiderID, Site, treatment, trial_age, mass_mg, dry_mg, moisture_per) %>% 
  unique() %>% 
  mutate(dry_microg = dry_mg * 1000,
         dry_microg_body_mg = dry_microg / mass_mg,
         moisture_per = as.numeric(moisture_per) / 100,
         treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud")) %>% 
  filter(! dry_mg == 0) 

# raw data
silk_sum <- silk %>% 
  group_by(Site, treatment) %>% 
  summarize(mean_silk = mean(dry_microg_body_mg), 
            se_silk = plotrix::std.error(dry_microg_body_mg))

silk_sum %>% 
  ggplot() +
  geom_point(aes(x = treatment, y = mean_silk, group = Site, color = Site)) +
  geom_errorbar(aes(x = treatment, ymin = mean_silk - se_silk, ymax = mean_silk + se_silk, group = Site, color = Site), width = 0.25) +
  xlab("Treatment") +
  ylab("Dry Silk Mass (g) Corrected by Body Mass (mg)") +
  scale_fill_manual(values = c("#1b9e77", "#d95f02"),
                     labels = c("Rural", "Urban")) +
  scale_color_manual(values = c("#1b9e77", "#d95f02"),
                     labels = c("Rural", "Urban")) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black"),
        axis.title = element_text(size = 14, color = "black"),
        legend.text = element_text(size = 14, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        legend.position = "top")

shapiro.test(log(silk$dry_microg_body_mg))
silk_model <- lm(log(dry_microg_body_mg) ~ Site * treatment, data = silk)
car::Anova(silk_model)
emmeans(silk_model, pairwise ~ treatment,  by = "Site")$contrasts
emmeans(silk_model, pairwise ~ Site,  by = "treatment")$contrasts

# not normal
silk_loud <- silk %>% 
  filter(treatment == "Loud")
kruskal.test(dry_microg_body_mg ~ Site, data = silk_loud)
silk_quiet <- silk %>% 
  filter(treatment == "Quiet")
kruskal.test(dry_microg_body_mg ~ Site, data = silk_quiet)

# assumptions
test_silk <- augment(silk_model, data = silk)
resid_silk <- ggplot(test_silk, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_silk$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_silk <- ggplot(test_silk, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14)) 

# predictions
nd = data.frame(expand_grid(Site = levels(factor(silk$Site)),
                treatment = levels(factor(silk$treatment))))

nd$fit <- predict(silk_model, newdata = nd, se.fit = TRUE, re.form = NA, type = "response")$fit
nd$SE <- predict(silk_model, newdata = nd, se.fit = TRUE, re.form = NA, type = "response")$se.fit
nd <- nd %>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"))

ggplot() +
  geom_jitter(aes(x = treatment, y = dry_microg_body_mg, group = Site, color = Site), size = 1, alpha = 0.5, width = 0.1, data = silk) +
  geom_line(aes(x = treatment, y = exp(fit), group = Site, color = Site), position = position_dodge(width = 0.25), size = 1, data = nd) +
  geom_point(aes(x = treatment, y = exp(fit), group = Site, color = Site), position = position_dodge(width = 0.25), size = 2.5, data = nd) +
  geom_errorbar(aes(x = treatment, ymin = exp(fit - SE), ymax = exp(fit + SE), group = Site, color = Site), width = 0.25, position = position_dodge(width = 0.25), size = 1, data = nd) +
  xlab("Treatment (4 Days)") +
  ylab("Dry Silk Mass (g) \nCorrected by Body Mass (mg)") +
  scale_color_manual("Collection Site", values = c("#1b9e77", "#d95f02")) +
  scale_y_continuous(limits = c(0, 26), breaks = c(0, 5, 10, 15, 20, 25), expand = c(0,0)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family = "sans"),
        axis.title = element_text(size = 14, color = "black", family = "sans"),
        legend.text = element_text(size = 14, color = "black", family = "sans"),
        legend.title = element_text(size = 14, color = "black", family = "sans"),
        legend.position = "top") 
```

```{r silk_moisture, echo = FALSE, message = FALSE}
# raw data
moist_sum <- silk %>% 
  group_by(Site, treatment) %>% 
  summarize(mean_moist = mean(moisture_per), 
            se_moist = plotrix::std.error(moisture_per)) %>% 
  mutate(treatment = factor(treatment),
         treatment = fct_relevel(treatment, "Quiet", "Loud"))

moist_sum %>% 
  ggplot() +
  geom_point(aes(x = treatment, y = mean_moist, group = Site, color = Site)) +
  geom_errorbar(aes(x = treatment, ymin = mean_moist - se_moist, ymax = mean_moist + se_moist, group = Site, color = Site), width = 0.25) +
  xlab("Treatment") +
  ylab("Percent Silk Moisture") +
  scale_fill_manual(values = c("#1b9e77", "#d95f02"),
                     labels = c("Rural", "Urban")) +
  scale_color_manual(values = c("#1b9e77", "#d95f02"),
                     labels = c("Rural", "Urban")) +
  theme_classic() +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 12, color = "black"),
        legend.position = "top")

shapiro.test(log(silk$moisture_per))
moist_model <- lm(log(moisture_per) ~ Site * treatment, data = silk)
car::Anova(moist_model)

# not normal
silk_urban <- silk %>% 
  filter(Site == "Urban")
kruskal.test(moisture_per ~ treatment, data = silk_urban)
silk_rural <- silk %>% 
  filter(Site == "Rural")
kruskal.test(moisture_per ~ treatment, data = silk_rural)

moist_model <- betareg(moisture_per ~ Site * treatment, data = silk)
car::Anova(moist_model)
emmeans(moist_model, pairwise ~ treatment,  by = "Site")$contrasts
emmeans(moist_model, pairwise ~ Site,  by = "treatment")$contrasts

# predictions
nd <- as.data.frame(allEffects(moist_model))$"Site:treatment"

ggplot() +
  geom_jitter(aes(x = treatment, y = moisture_per, group = Site, color = Site), size = 1, alpha = 0.5, width = 0.1, data = silk) +
  geom_line(aes(x = treatment, y = fit, group = Site, color = Site), position = position_dodge(width = 0.25), size = 1, data = nd) +
  geom_point(aes(x = treatment, y = fit, group = Site, color = Site), position = position_dodge(width = 0.25), size = 2.5, data = nd) +
  geom_errorbar(aes(x = treatment, ymin = fit - se, ymax = fit + se, group = Site, color = Site), width = 0.25, position = position_dodge(width = 0.25), size = 1, data = nd) +
  xlab("Treatment (4 Days)") +
  ylab("Proportion of Silk Moisture") +
  scale_color_manual("Collection Site", values = c("#1b9e77", "#d95f02")) +
  scale_y_continuous(limits = c(0, 0.6), breaks = c(0, 0.2, 0.4, 0.6), expand = c(0,0)) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black", family = "sans"),
        axis.title = element_text(size = 14, color = "black", family = "sans"),
        legend.text = element_text(size = 14, color = "black", family = "sans"),
        legend.title = element_text(size = 14, color = "black", family = "sans"),
        legend.position = "top") 

```

```{r silk stats, echo = FALSE, message = FALSE}
silk_stats <- read.csv(file = "tables/silk_table.csv", header = TRUE) %>% 
  mutate(dependent = factor(dependent),
         dependent = fct_recode(dependent, "Dry Silk Mass (g) per Body Mass (mg)" = "silk_mass", 
                            "Prop. Silk Moisture" = "silk_moist"),
         test = factor(test), 
         test = fct_recode(test, "ANOVA" = "lm",
                                   "Beta Regression " = "beta"),
         independent = factor(independent),
         independent = fct_recode(independent, "Collection Site" = "Site",
                               "Treatment" = "Treatment",
                               "Collection Site x Treatment" = "Site_Treatment"),
         df = factor(df),
         df = fct_recode(df, " 56" = "56", "56" = "_56"),
         p_value = factor(p_value),
         p_value = fct_recode(p_value, "   0.159" = "0.1593",
                        "   0.817" = "0.8169",
                        "   0.226" = "0.2262",
                        "   0.435" = "0.43468",
                        "   0.078 ." = "0.07844",
                        "   0.144" = "0.14418")) 

colnames(silk_stats) <- c('Dependent Variable','Test', 'Residual DF', 'Independent Variable', 'Test Statistic', 'P-Value')

flextable(silk_stats[, 1:6]) %>% 
  autofit() %>% 
  merge_v(j = c('Dependent Variable', 'Test', 'Residual DF'), part = "body") %>% 
  theme_vanilla() %>% 
  hline(i = c("1", "2", "4", "5"), 
        j = c("Independent Variable", "Test Statistic", "P-Value"), 
        part = "body", 
        border = officer::fp_border(width = 0, color = "black")) %>% 
  bold(bold = TRUE, part = "header") %>% 
  fontsize(size = 10, part = "all") %>% 
  align(align = "left", part = "all") %>%
  valign(valign = "top", part = "all") %>% 
    footnote(i = c(1), j = 2, part = "body", ref_symbols = "a", value = as_paragraph("Test statistic: F-value")) %>%
  footnote(i = c(4), j = 2, ref_symbols = "b", value = as_paragraph("Test statistic: Chi-squared value")) #%>% 
  #save_as_image(path = here::here("silk_table.png"))

silk_stats2 <- read.csv(file = "tables/multicomp_silk.csv", header = TRUE) %>% 
  mutate(Dependent = factor(Dependent),
         Dependent = fct_recode(Dependent, "Dry Silk Mass (g) per Body Mass (mg)" = "silk_mass", 
                            "Prop. Silk Moisture" = "silk_moist"),
         Comparison = factor(Comparison),
         Comparison = fct_recode(Comparison, "Collection Site" = "Site"),
         df = factor(df),
         df = fct_recode(df, " 56" = "56", "56" = "_56"),
         p_value = factor(p_value),
         p_value = fct_recode(p_value, "   0.887" = "0.8865",
                        "   0.066 ." = "0.0662",
                        "   0.022 *" = "0.022",
                        "   0.798" = "0.7978"))

colnames(silk_stats2) <- c('Dependent Variable','Residual DF', 'Comparison', 'Level', 'Test Statistic', 'P-Value')

flextable(silk_stats2[, 1:6]) %>% 
  autofit() %>% 
  merge_v(j = c('Dependent Variable', 'Residual DF', 'Comparison'), part = "body") %>% 
  theme_vanilla() %>% 
  hline(i = c("1", "3"), 
        j = c("Level", "Test Statistic", "P-Value"), 
        part = "body", 
        border = officer::fp_border(width = 0, color = "black")) %>% 
  bold(bold = TRUE, part = "header") %>% 
  fontsize(size = 10, part = "all") %>% 
  align(align = "left", part = "all") %>%
  valign(valign = "top", part = "all") %>% 
    footnote(i = c(1, 2), j = 5, part = "body", ref_symbols = "a", value = as_paragraph("Test statistic: t-ratio")) %>%
  footnote(i = c(3, 4), j = 5, ref_symbols = "b", value = as_paragraph("Test statistic: z-ratio")) #%>% 
  #save_as_image(path = here::here("silk_table_multicomp.png"))
```
